### 2019-06-05 paper.tex
Add files via upload
These are the tex and bib files for our LaTex document. Feel free to alter the formatting as desired.

\documentclass[12pt]{article}
\usepackage{amsmath}%
\usepackage{amssymb}%
\usepackage{multicol}
\usepackage{graphicx,epsfig}%
\usepackage[margin=1in]{geometry}
\usepackage{rotating}%
\usepackage{url}
\usepackage[notes,backend=bibtex]{biblatex-chicago}
\bibliography{prepWork}
\usepackage{epsfig}%
\usepackage{epstopdf}%
\usepackage{varwidth}
\usepackage{lscape}%
\usepackage{color}
\usepackage[hang,flushmargin]{footmisc} 
\pdfminorversion 3
\usepackage{pbox}

\newcommand{\hilt}[1]{\colorbox{green}{#1}}
\usepackage{setspace}
\usepackage{adjustbox}
\def\x{\mathbf{x}}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\newcommand{\tcr}{\textcolor{red}}
\newcommand{\tcb}{\textcolor{blue}}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\DeclareMathOperator*{\argmin}{argmin} 
\renewcommand{\baselinestretch}{1.5}
\usepackage{tabularx}

\usepackage{bibentry}

\title{S19: REU Paper}
\author{Emily Slaughter, Gennie Mansi }

\begin{document}

\maketitle

\clearpage

\tableofcontents

\clearpage

%%%%%%%%%%%%%%%%%%%

\clearpage

%%%%%%%%%%%%%%%%%%%%
\section{References}

\printbibliography

\end{document}

### 2019-06-07 paper.tex
Update paper.tex
Add files via upload
Updated to contain a short description of our project and our motivation

@@
 \usepackage[notes,backend=bibtex]{biblatex-chicago}
-\bibliography{prepWork}
+\bibliography{paper}
 \usepackage{epsfig}%
@@
 
-\title{S19: REU Paper}
+\title{S19: REU Research Document}
 \author{Emily Slaughter, Gennie Mansi }
@@
 %%%%%%%%%%%%%%%%%%%
+\section{Motivation and project overview}
+
+Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed teams.
+As code is written and the project develops, various design decisions are made, which impact both existing and future code.
+Documentation of design decisions and the rational behind those decisions is dependent on the developer and is often recorded or dispersed between a formal document and comments in the code itself.
+However, documentation is often not written, read, or updated, causing developers to depend largely on the code rather than existing documentation.
+
+We are working to help create a tool that uses mixed human-AI authoring of code patterns in order document and update code, thus enabling developers to efficiently and accurately apply and maintain a unified set of design rules.
+There are an infinite number of patterns that could be found in a given code base; therefore, the crux of the problem lies in determining which patterns in the given code should be used to train the machine learning algorithm.
+Finding an excessive number of non-existent rules or not finding important or obvious rules would discourage developers from using the tool to document their code.
+Hence our focus this summer will be on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.
 

### 2019-06-14 paper.tex
Add files via upload
LaTEx file with updates as per instructions for week #2

@@
 \usepackage{url}
-\usepackage[notes,backend=bibtex]{biblatex-chicago}
+\usepackage[backend=bibtex, citestyle=ieee]{biblatex}
 \bibliography{paper}
@@
 %%%%%%%%%%%%%%%%%%%
-\section{Motivation and project overview}
+\section{Abstract}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
 
@@
 
+There are essentially three distinct situations in which such a tool may be used.
+Each situation offers its own challenges and requires different operational capabilities on the part of the tool.
+The first situation is that in which a developer who is experienced with a given code base is trying to author rules or verify that certain rules have been followed.
+The second situation is one in which a developer who is not as familiar with a code base but still has some base knowledge of its contents and general design is trying to explore possible rules.
+It may be the case that the developer just needs to see a rule in order to recognize is correctness or applicability, but she on her own might not be able to produce an accurate rule.
+A developer in this situation may be able to provide useful feedback on which rules are helpful and relevant to a given code base.
+The final situation is that of a developer who is not familiar with a code base at all and needs rule suggestions both to understand the structure of the code and to ensure it adheres to a single standard.
+In such a situation, the developer may even be interested in looking for examples on what kind of design decisions were previously made to which she should adhere.
+
+ ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view correct examples and violations of rules in a given code base in real time \cite{MehrpurEtAl2019}.
+In the first situation a tool like the ActiveDocumentation plug-in would be able to help the developer author, check, and fix rules, efficiently and in real time.
+Thus, the second and third cases provide more interesting challenges.
+LaToza et al explored finding design patterns in an HTML document in order to perform code prediction \cite{LaTozaEtAl2019}.
+However, they did not try to identify design rules that might explain that pattern nor did they integrate information from sources outside of the code base such as cursor information or search history.
+We seek to develop a tool that combines the rule-authoring and live-update features from ActiveDocumentation with pattern finding properties.
+We also wish to explore how information from outside of the code base could be used to inform what patterns are identified.
+Since ActiveDocumentation can help those who understand a code base write rules and check for correct examples and violations of that rule, a natural next step is to work on a tool for a developer who might have some knowledge about a code base that is not comprehensive (i.e.
+the second situation).
+This forms a natural bridge between a tool that is used by a developer who simply needs to author rules for a code base she is familiar with (the first situation), and a tool that is used by someone who is completely unfamiliar with a code base and cannot provide helpful or accurate feedback about suggested rules.
+Thus, in this paper, we focus on developing a tool to help a developer who finds herself in the second situation.
 \clearpage
+
+%%%%%%%%%%%%%%%%%%%
+\section{Tool design and development}
+There are several major considerations even when we narrow our focus to a developer in the second situation.
+These considerations divide generally into considerations of what kinds of data are available and helpful for suggesting rules and how these kinds of data can be utilized to make relevant design rule suggestions.
+
+There are sundry sources of data available that can and do provide information about the code base and what sections of the code in which the developer might be most interested.
+The most obvious source of information about the code is the code itself.
+Using a tool called srcML, the code can be put in a specific XML format that can then be searched using XPaths.
+Thus we can identify all kinds of information about the code itself, including function and class names and declarations, member variables, and relationships between classes like child and parent classes.
+Information is also available from the IDE itself.
+Such information can include the cursor's current and previous location, the user's search history, and which file windows are currently open in the project.
+Finally, the tool itself could be a possible source of information.
+For example, information about existing rules may be used to help improve the relevancy of the design rules presented to the developer.
+
+There are a couple of approaches that could be taken with respect to different approaches to ensure relevant design rule suggestions.
+One way of viewing this challenge is to view it as a source of natural language programming (NLP) problem.
+One group of researchers were trying to improve code suggestions and viewed their challenge as analogous to a more traditional NLP problem of trying to fill in a missing word in a sentence.
+They developed a statistical language model to aid in providing suggestions for different code snippets \cite{RaychevEtAl2014}.
+We could think of our challenge as analogous to an NLP problem that aims to outline to a corpus of text or maybe, even more abstractly, find rhetorical devices in a text.
+Alternatively, we could simply rely more on traditional papers and research that have been conducted in this area that do not rely on NLP techniques to provide solutions.
+Both perspective may prove useful in the initial stages of research that entail exploring different ways that information is stored and what information about developer activity has seemed most helpful in designing related tools.
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%
+\section{Product description}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%
+\section{Methodology}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%
+\section{User study}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%
+\section{Related works}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%
 

### 2019-06-14 paper.tex
edits, no additions yet

@@
 As code is written and the project develops, various design decisions are made, which impact both existing and future code.
-Documentation of design decisions and the rational behind those decisions is dependent on the developer and is often recorded or dispersed between a formal document and comments in the code itself.
-However, documentation is often not written, read, or updated, causing developers to depend largely on the code rather than existing documentation.
+Documentation of design decisions and the rationale behind those decisions is dependent on the developer and is often recorded or dispersed between a formal document and comments in the code itself.
+However, documentation is often not written, read, or updated, causing \textbf{newcomers to a project} to depend largely on the code rather than existing documentation \textbf{to understand such project-specific design rules}.
 
-We are working to help create a tool that uses mixed human-AI authoring of code patterns in order document and update code, thus enabling developers to efficiently and accurately apply and maintain a unified set of design rules.
-There are an infinite number of patterns that could be found in a given code base; therefore, the crux of the problem lies in determining which patterns in the given code should be used to train the machine learning algorithm.
-Finding an excessive number of non-existent rules or not finding important or obvious rules would discourage developers from using the tool to document their code.
-Hence our focus this summer will be on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.
+\textbf{We are working to create a tool that enables mixed human-AI authoring of code patterns, thus facilitating active documentation and maintenance of code and allowing developers to efficiently and accurately apply and maintain a unified set of design rules.
+There are an exponential number of patterns that could be found in a given code base, and some rules have greater relevance than others.
+Finding an excessive number of non-existent rules or missing important or obvious rules would discourage developers from using the tool to document their code.
+Hence the crux of the problem, and therefore our focus this summer, is to intelligently determine which patterns in a codebase of any language should be used to train the machine learning algorithm.}
 
@@
 A developer in this situation may be able to provide useful feedback on which rules are helpful and relevant to a given code base.
-The final situation is that of a developer who is not familiar with a code base at all and needs rule suggestions both to understand the structure of the code and to ensure it adheres to a single standard.
-In such a situation, the developer may even be interested in looking for examples on what kind of design decisions were previously made to which she should adhere.
+The final situation is that of a developer who is not familiar with a code base at all and needs rule suggestions both to understand the structure of the code and to ensure \textbf{she adheres to its standards.
+In such a situation, the developer may even be interested in looking for examples on what kind of design decisions were previously made.}
 
- ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view correct examples and violations of rules in a given code base in real time \cite{MehrpurEtAl2019}.
-In the first situation a tool like the ActiveDocumentation plug-in would be able to help the developer author, check, and fix rules, efficiently and in real time.
-Thus, the second and third cases provide more interesting challenges.
+ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view \textbf{examples that adhere to or violate rules in a given code base} in real time \cite{MehrpurEtAl2019}.
+In the first situation, a tool like the ActiveDocumentation plug-in would be able to help the developer author, check, and fix rules, efficiently and in real time.
+\textbf{The second and third cases, however,} provide more interesting challenges.
 LaToza et al explored finding design patterns in an HTML document in order to perform code prediction \cite{LaTozaEtAl2019}.
 However, they did not try to identify design rules that might explain that pattern nor did they integrate information from sources outside of the code base such as cursor information or search history.
+
 We seek to develop a tool that combines the rule-authoring and live-update features from ActiveDocumentation with pattern finding properties.
@@
 
-There are sundry sources of data available that can and do provide information about the code base and what sections of the code in which the developer might be most interested.
+There are sundry sources of data available \textbf{that provide information about the code base and sections} in which the developer might be most interested.
 The most obvious source of information about the code is the code itself.
-Using a tool called srcML, the code can be put in a specific XML format that can then be searched using XPaths.
+Using a tool called srcML, the code can be put \textbf{into} XML format that can then be searched using XPath.
 Thus we can identify all kinds of information about the code itself, including function and class names and declarations, member variables, and relationships between classes like child and parent classes.
 Information is also available from the IDE itself.
-Such information can include the cursor's current and previous location, the user's search history, and which file windows are currently open in the project.
+Such information can include the cursor's current and previous locations, the user's search history, and which file windows are currently open in the project.
 Finally, the tool itself could be a possible source of information.
@@
 
-There are a couple of approaches that could be taken with respect to different approaches to ensure relevant design rule suggestions.
-One way of viewing this challenge is to view it as a source of natural language programming (NLP) problem.
+\textbf{There are a couple of approaches that could be taken to ensure relevant design rule suggestions.} One way of viewing this challenge is to view it as a source of natural language programming (NLP) problem.
 One group of researchers were trying to improve code suggestions and viewed their challenge as analogous to a more traditional NLP problem of trying to fill in a missing word in a sentence.
 They developed a statistical language model to aid in providing suggestions for different code snippets \cite{RaychevEtAl2014}.
-We could think of our challenge as analogous to an NLP problem that aims to outline to a corpus of text or maybe, even more abstractly, find rhetorical devices in a text.
+We could think of our challenge as analogous to an NLP problem that aims to outline a corpus of text or maybe, even more abstractly, find rhetorical devices in a text.
 Alternatively, we could simply rely more on traditional papers and research that have been conducted in this area that do not rely on NLP techniques to provide solutions.
-Both perspective may prove useful in the initial stages of research that entail exploring different ways that information is stored and what information about developer activity has seemed most helpful in designing related tools.
+Both perspectives may prove useful in the initial stages of research that entail exploring different ways that information is stored and what information about developer activity has seemed most helpful in designing related tools.
 

### 2019-06-17 paper.tex
edit & addition

@@
 Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed teams.
-As code is written and the project develops, various design decisions are made, which impact both existing and future code.
+As code is written and a project develops, various design decisions are made, which impact both existing and future code.
 Documentation of design decisions and the rationale behind those decisions is dependent on the developer and is often recorded or dispersed between a formal document and comments in the code itself.
-However, documentation is often not written, read, or updated, causing \textbf{newcomers to a project} to depend largely on the code rather than existing documentation \textbf{to understand such project-specific design rules}.
+However, documentation is often not written, read, or updated, and coworkers are not always a reliable resource.
+Ko et al found that during software development, the information most frequently sought by developers was about artifacts and coworkers, and furthermore that tasks were often deferred because the only source of knowledge was coworkers who were unavailable \cite{KoEtAl2007}.
+Lack of documentation ultimately causes newcomers to a project to depend largely on the code rather than existing documentation to understand such project-specific design rules.
 
-\textbf{We are working to create a tool that enables mixed human-AI authoring of code patterns, thus facilitating active documentation and maintenance of code and allowing developers to efficiently and accurately apply and maintain a unified set of design rules.
+We are working to create a tool that enables mixed human-AI authoring of code patterns, thus facilitating active documentation and maintenance of code and allowing developers to efficiently and accurately apply and maintain a unified set of design rules.
 There are an exponential number of patterns that could be found in a given code base, and some rules have greater relevance than others.
 Finding an excessive number of non-existent rules or missing important or obvious rules would discourage developers from using the tool to document their code.
-Hence the crux of the problem, and therefore our focus this summer, is to intelligently determine which patterns in a codebase of any language should be used to train the machine learning algorithm.}
+Hence the crux of the problem, and therefore our focus this summer, is to intelligently determine which patterns in a codebase of any language should be used to train the machine learning algorithm.
 
@@
 A developer in this situation may be able to provide useful feedback on which rules are helpful and relevant to a given code base.
-The final situation is that of a developer who is not familiar with a code base at all and needs rule suggestions both to understand the structure of the code and to ensure \textbf{she adheres to its standards.
-In such a situation, the developer may even be interested in looking for examples on what kind of design decisions were previously made.}
+The final situation is that of a developer who is not familiar with a code base at all and needs rule suggestions both to understand the structure of the code and to ensure she adheres to its standards.
+In such a situation, the developer may even be interested in looking for examples on what kind of design decisions were previously made.
 
-ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view \textbf{examples that adhere to or violate rules in a given code base} in real time \cite{MehrpurEtAl2019}.
+ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view examples that adhere to or violate rules in a given code base in real time \cite{MehrpurEtAl2019}.
 In the first situation, a tool like the ActiveDocumentation plug-in would be able to help the developer author, check, and fix rules, efficiently and in real time.
-\textbf{The second and third cases, however,} provide more interesting challenges.
+The second and third cases, however, provide more interesting challenges.
 LaToza et al explored finding design patterns in an HTML document in order to perform code prediction \cite{LaTozaEtAl2019}.
@@
 Thus, in this paper, we focus on developing a tool to help a developer who finds herself in the second situation.
+
 \clearpage
@@
 
-There are sundry sources of data available \textbf{that provide information about the code base and sections} in which the developer might be most interested.
+There are sundry sources of data available that provide information about the code base and sections in which the developer might be most interested.
 The most obvious source of information about the code is the code itself.
-Using a tool called srcML, the code can be put \textbf{into} XML format that can then be searched using XPath.
+Using a tool called srcML, the code can be put into XML format that can then be searched using XPath.
 Thus we can identify all kinds of information about the code itself, including function and class names and declarations, member variables, and relationships between classes like child and parent classes.
@@
 
-\textbf{There are a couple of approaches that could be taken to ensure relevant design rule suggestions.} One way of viewing this challenge is to view it as a source of natural language programming (NLP) problem.
+When considering what makes a rule relevant and how to automate the process of finding relevant rules, it's important to question how developers currently find relevant rules.
+According to a degree-of-interest (DOI) model developed by Fritz et al, a developer's activity can in fact be used as a proxy for their knowledge of code.
+Initially, the DOI model was defined in terms of two components: frequency and recency.
+The frequency with which a developer interacted with an element increased that element's DOI value, while the recency with which a developer interacted with an element decayed that element's DOI value.
+It was found that in addition to frequency and recency, however, other factors such as authorship of code, authorship duration, code stability, existence of code patterns, role of elements in a program, task locality, work experience, and type of activity are all important factors that affect a developer's program structure knowledge as well \cite{FritzEtAl2007}.
+
+There are a couple of approaches that could be taken to ensure relevant design rule suggestions.
+One way of viewing this challenge is to view it as a source of natural language programming (NLP) problem.
 One group of researchers were trying to improve code suggestions and viewed their challenge as analogous to a more traditional NLP problem of trying to fill in a missing word in a sentence.
@@
 
+Through what is called implicit group memory, Hipikat is a client-server system that automates the mentor-like relationship that develops between developers who are new to a project and senior developers who watch over the newcomers and pass down knowledge.
+Hipikat learn from four types of artifacts and communications stored in a project's history: bug and feature descriptions, source file revisions, messages posted on developer forums, and other project documents.
+Artifacts may be queried, and the artifact database may be searched \cite{CubranicAndMurphy2003}.
+
+Mylar is a tool that exists within the Eclipse IDE and encodes a programmer's activity with code into a degree-of-interest model that can then be used to filter information in a program that may be related to the task that a developer is completing.
+Programmer activity is defined as selections and editing of code.
+This model focuses on individual program elements without taking into account the possible structural relationships that may exist between program elements \cite{KerstenEtAl2005}.
+
 \clearpage

### 2019-06-20 paper.tex
Week 3 Updates
-Changed structure as well as I could remember to fit Huzefa's recommendations
-Mostly pulled things out of the introduction and shifted sections in the paper around
-Related works had info put in it; more info may be placed here as we read more papers
-Removed user study section since realistically we will not be conducting a user study by the end of the summer

--- 2019-06-14 paper.tex
@@
 %%%%%%%%%%%%%%%%%%%
-\section{Abstract}
+\section{Abstract} \label{abstract}
 
@@
 %%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction} \label{intro}
 
@@
 As code is written and the project develops, various design decisions are made, which impact both existing and future code.
-Documentation of design decisions and the rational behind those decisions is dependent on the developer and is often recorded or dispersed between a formal document and comments in the code itself.
-However, documentation is often not written, read, or updated, causing developers to depend largely on the code rather than existing documentation.
+Documentation of design decisions and the rational behind those decisions is dependent on the developer and is often recorded or dispersed between several disparate locations, including a formal document, comments in the code, and the developers themselves.
+However, documentation is often not written, read, or updated, causing developers to depend largely on the code and other sources of information rather than explicit, written documentation.
 
-We are working to help create a tool that uses mixed human-AI authoring of code patterns in order document and update code, thus enabling developers to efficiently and accurately apply and maintain a unified set of design rules.
+Ideally, as code is authored or modified, it should follow previous design rules use to author prior code.
+The \textit{design rules} for a project is the set of choices about the code's design and how those choices were implemented.
+Several sources of information, including search history, cursor location, event logs, debugger information, and the code itself can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest.
+Some information about design rules may only be recorded in the memories of co-workers, and thus access to this kind of information is also critical for developers trying to understand and use an existing code base.
+
+Mixed human-AI authoring of code patterns can greatly assist developers to efficiently and accurately develop and maintain a unified set of rules.
 There are an infinite number of patterns that could be found in a given code base; therefore, the crux of the problem lies in determining which patterns in the given code should be used to train the machine learning algorithm.
-Finding an excessive number of non-existent rules or not finding important or obvious rules would discourage developers from using the tool to document their code.
-Hence our focus this summer will be on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.
+Hence our focus is on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.
 
-There are essentially three distinct situations in which such a tool may be used.
-Each situation offers its own challenges and requires different operational capabilities on the part of the tool.
-The first situation is that in which a developer who is experienced with a given code base is trying to author rules or verify that certain rules have been followed.
-The second situation is one in which a developer who is not as familiar with a code base but still has some base knowledge of its contents and general design is trying to explore possible rules.
-It may be the case that the developer just needs to see a rule in order to recognize is correctness or applicability, but she on her own might not be able to produce an accurate rule.
-A developer in this situation may be able to provide useful feedback on which rules are helpful and relevant to a given code base.
-The final situation is that of a developer who is not familiar with a code base at all and needs rule suggestions both to understand the structure of the code and to ensure it adheres to a single standard.
-In such a situation, the developer may even be interested in looking for examples on what kind of design decisions were previously made to which she should adhere.
+We explore how information from outside of the code base could be used to inform what patterns are identified.We seek to develop a tool that combines that has both automatic and manual rule-authoring capabilities.
+It should also automatically provide live updates with examples and violations of authored design rules.
+Ultimately, such a tool will greatly increase the amount of up-to-date documentation available to developers.
 
- ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view correct examples and violations of rules in a given code base in real time \cite{MehrpurEtAl2019}.
-In the first situation a tool like the ActiveDocumentation plug-in would be able to help the developer author, check, and fix rules, efficiently and in real time.
-Thus, the second and third cases provide more interesting challenges.
-LaToza et al explored finding design patterns in an HTML document in order to perform code prediction \cite{LaTozaEtAl2019}.
-However, they did not try to identify design rules that might explain that pattern nor did they integrate information from sources outside of the code base such as cursor information or search history.
-We seek to develop a tool that combines the rule-authoring and live-update features from ActiveDocumentation with pattern finding properties.
-We also wish to explore how information from outside of the code base could be used to inform what patterns are identified.
-Since ActiveDocumentation can help those who understand a code base write rules and check for correct examples and violations of that rule, a natural next step is to work on a tool for a developer who might have some knowledge about a code base that is not comprehensive (i.e.
-the second situation).
-This forms a natural bridge between a tool that is used by a developer who simply needs to author rules for a code base she is familiar with (the first situation), and a tool that is used by someone who is completely unfamiliar with a code base and cannot provide helpful or accurate feedback about suggested rules.
-Thus, in this paper, we focus on developing a tool to help a developer who finds herself in the second situation.
  \clearpage
@@
 %%%%%%%%%%%%%%%%%%%
-\section{Tool design and development}
+\section{Methods}\label{methods}
+
+\subsection{Problem Description} \label{probDesc}
+
+Given the code for a project and some external information such as cursor information, we wish to derive a set of most likely and relevant design rules.
+We will then integrate our algorithm for mining these design rules into an interface that allows developers to seamlessly mine and write design rules and to see violations and correct examples of these rules.
+
+When considering our task, there exist two significant considerations: (a) what kinds of data are available and helpful for suggesting rules, and (b) what kind of algorithm can be utilized with these sources of data in order to make relevant design rule suggestions.
+We will begin by first addressing different sources of information that are available and most useful for our purpose.
+Then, we will proceed to discuss our algorithm for design rule mining.
+
+\subsection{Assumptions about the user} \label{assumptions}
+
+Developers can be divided into three categories with respect to their familiarity with a project or code base.
+First, a developer may be experienced with a given code base.
+She would have a thorough understanding of the project, its objectives, and its implementation.
+She is in a position that allows her to author design rules and verify that certain rules have been followed through the project.
+Second, a developer may be partially knowledgable about a project and its implementation.
+Such a developer may have a general familiarity with the code and its implementations, but is not able to easily or confidently author design rules or may simply wish to explore possible existing design rules.
+On her own she is not be able to produce an accurate rule, but might be able to see a rule and provide useful feedback on its correctness or relevancy.
+Finally, a developer may be completely unfamiliar with a code base.
+Existing design rules and documents would be extremely helpful in helping her understand the structure of the code.
+She may also need to frequently consult co-workers about code standards and patterns if there is a significant lack of written documentation.
+In such a situation, the developer may even be interested in looking for examples on what kind of existing design rules to which she should adhere.
+
+ Work has already been completed with regards to the first category, and while much research has been done in code suggestion, completely automated design rule generation seems largely unexplored (see Section~\ref{relatedWorks}).
+Therefore, an algorithm developed with the second category of developers in mind forms a natural bridge between human authored design rules and completely automated rule authoring.
+Consequently, we assume the developers for which we are designing our algorithm have some general familiarity with the code and can identify proper design rules if supplied with a set of rules to consider.
+Thus, feedback form the developer about hypothesized rules is dependable, enabling mixed human-AI rule authoring.
+
+\subsection{Sources of Information} \label{infoSrcs}
+
+Part of knowing which sources are most useful for deriving information about design rules is understanding where developers themselves look for information about a project and what kinds of information are useful to programmers.
+
+\subsection{Possible sources}
+
+Several studies have demonstrated that as developers work and explore a project, they try to answer high-level questions about what, why, and how code causes different program states as they try to complete a task \cite{SadowskiEtAl2015, LaTozaMyers2010, LaTozaEtAl2007}.
+Researchers who investigated how programmers read and explore code have found that programmers' activities include checking implementation details, checking common style, and browsing.
+Programmers also performed code search to understand various dependencies within and between projects, why something is failing, and the side effects of a proposed changed \cite{SadowskiEtAl2015}.
+
+Ko et al investigate what sources of information developers use to accomplish a task and how that information affects developers' workflow throughout the day.
+They report that developers look at a variety of sources to accomplish a task, including check-in logs, bug reports, content management systems, version control systems, and other coworkers.
+Additionally, they identify knowledge about design and program behavior as the type of information that is most often deferred since unavailable coworkers are often the only source of knowledge.
+Developers sought out coworkers most often when there are information needs with regards to code design.
+Other questions to coworkers centered around following the team's conventions.
+Developers asked specific questions regarding what code caused different program states and behaviors and what statically related to the code of interest, but pursued the answers to these questions by starting with a hypothesis that they largely developed by using their intuition, asking coworkers, looking for execution logs, scouring bug reports, and using the debugger.
+They then often refined their hypothesis by using the search tool to answer questions about which sections of code performed similar operations \cite{KoEtAl2007}.
+
+Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree of interest model to reflect developers' knowledge of code \cite{FritzEtAl2007}.
+The researchers' model was based on the total number of interactions the programmer has with an element and the recency of that interaction.
+Other factors they identified that could be used to improve their model included authorship of program elements, the role of elements, and the task being performed \cite{FritzEtAl2007}.
+
+Based off of  these findings, we identified the debugger (?), code base, cursor location and search histories, and the developer herself as the most pertinent and accessible sources of information for our algorithm.
+
+\textit{Debugger.} [Insert something later when we know what exactly we will be using about how we are using the debugger as a source of information ]
+
+\textit{Cursor location.} [Insert something later when we know what exactly we will be using about how we are using the cursor location as a source of information ]
+
+\textit{Search history.} [Insert something later when we know what exactly we will be using about how we are using the search history as a source of information ]
+
+\textit{Developer.} [Insert something later when we know what exactly we will be using about how we are using the developer as a source of information ]
+
+\subsection{Algorithm} \label{algm}
+
+\subsubsection{Filtering information}
+\subsubsection{Identifying token}
+\subsubsection{Generating queries}
+\subsubsection{Selecting queries to present to user}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%
+
+\section{Tool interface} \label{toolInterface}
 There are several major considerations even when we narrow our focus to a developer in the second situation.
@@
 \clearpage
+
 %%%%%%%%%%%%%%%%%%%
-\section{Product description}
+
+\section{Related works}\label{relatedWorks}
+
+Many tools and methods have been devised to augment programmers' ability to accomplish a task including code recommender systems for novices \cite{HartmannEtAl2010}, search tools for identifying bugs \cite{HovemeyerPugh2004}, search tools for identifying relevant API functions and the sections of code that need to be altered \cite{RongEtAl2016}, and code suggestion \cite{RaychevEtAl2014}.
+However, one area that seems largely unexplored is tools that facilitate the documentation of code.
+
+Some researchers developed a tool to help a person who is new to an open-source software project find relevant artifacts to a project in order to facilitate their ability to more quickly perform a given task.
+They consider all of the previously produced material, including versions of the source, the bugs, archived electronic communication, and web documents, to suggest possibly relevant sources of information to a user \cite{CubranicMurphy2003}.
+
+LaToza et al explored finding design patterns in an HTML document in order to perform code prediction \cite{LaTozaEtAl2019}.
+However, their tool does not identify design rules that might explain that pattern.
+ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view correct examples and violations of rules in a given code base in real time \cite{MehrpurEtAl2019}.
+The ActiveDocumentation plug-in helps the developer author, check, and fix rules, efficiently and in real time.
+It automatically updates its interface with correct examples and violations of design rules written in the program \cite{MehrpurEtAl2019}.
+Neither of these tools integrates information from sources outside of the code base such as cursor information or search history.
+Mylar is a tool designed for the Eclipse IDE that tries to highlight file names and code segments that are most likely to contain relevant information for a developer's current task.
+The highlighting is based off a model that depends on which elements of the code have been edited and accessed most recently \cite{KerstenMurphy2005}.
 
@@
 %%%%%%%%%%%%%%%%%%%
-\section{Methodology}
+\section{Discussion}\label{disc}
 
-\clearpage
+It might be helpful to adapt our tool to be able to work with team environments.
 
-%%%%%%%%%%%%%%%%%%%
-\section{User study}
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%
-\section{Related works}
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+I don't really feel like discussing things any more.
+Why is this the only part that is called the discussion?
+I mean, what has been the rest of everything that has been written?
+Or did you just skip here?
+Is that why it has been called ``discussion"?
 
@@
 
+\section{Discussion}\label{disc}
+
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%
-\section{References}
+\section{References}\label{references}
 

### 2019-06-24 paper.tex
Add files via upload

@@
 \title{S19: REU Research Document}
-\author{Emily Slaughter, Gennie Mansi }
+\author{Emily Slaughter, Gennie Mansi}
 
@@
 Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed teams.
-As code is written and the project develops, various design decisions are made, which impact both existing and future code.
-Documentation of design decisions and the rational behind those decisions is dependent on the developer and is often recorded or dispersed between several disparate locations, including a formal document, comments in the code, and the developers themselves.
-However, documentation is often not written, read, or updated, causing developers to depend largely on the code and other sources of information rather than explicit, written documentation.
+As code is written and the project develops, various design decisions are made, which impact both existing and future code: ideally, as code is authored or modified, it should follow design rules used to author prior code.
+The \textit{design rules} for a project are the set of choices about the code's design and their implementation.
+Documentation of design rules and the rationale behind them is dependent on the developer, and when it is recorded, it is often dispersed among several disparate locations, including a formal document, comments in the code, and the developers themselves.
+However, documentation is often not written, read, or updated, and coworkers are not always a reliable resource \cite{KoEtAl2007}.
+Lack of documentation ultimately causes newcomers to a project to depend largely on the code rather than explicit, written documentation to understand such project-specific design rules.
 
-Ideally, as code is authored or modified, it should follow previous design rules use to author prior code.
-The \textit{design rules} for a project is the set of choices about the code's design and how those choices were implemented.
-Several sources of information, including search history, cursor location, event logs, debugger information, and the code itself can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest.
-Some information about design rules may only be recorded in the memories of co-workers, and thus access to this kind of information is also critical for developers trying to understand and use an existing code base.
+A tool that mines and recommends design rules has the potential to facilitate active documentation of code, allowing developers to efficiently and accurately apply and maintain a unified set of design rules.
+There are an exponential number of patterns that could be found in a given code base, and some rules have greater relevance than others.
+Finding an excessive number of non-existent rules or missing important rules would discourage developers from using the tool to document their code.
+Hence our focus is to intelligently determine which patterns in a codebase of any language are most meaningful as rules and how to find them reasonably quickly.
 
-Mixed human-AI authoring of code patterns can greatly assist developers to efficiently and accurately develop and maintain a unified set of rules.
-There are an infinite number of patterns that could be found in a given code base; therefore, the crux of the problem lies in determining which patterns in the given code should be used to train the machine learning algorithm.
-Hence our focus is on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.
+Several sources of information in addition to the code itself, including search history, cursor location, event logs, and debugger information can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest.
+We explore how this information from outside of the code base can be combined with the code base itself to inform what patterns are identified.
+Ultimately, such a tool will greatly increase the amount of up-to-date documentation available to developers.
+We seek to develop a tool that automates the manual rule-authoring capabilities of ActiveDocumentation \cite{MehrpurEtAl2019} and preserves its live-update features.
 
-We explore how information from outside of the code base could be used to inform what patterns are identified.We seek to develop a tool that combines that has both automatic and manual rule-authoring capabilities.
-It should also automatically provide live updates with examples and violations of authored design rules.
-Ultimately, such a tool will greatly increase the amount of up-to-date documentation available to developers.
+Association rule mining? Some brief description of our algorithm?
 
@@
 First, a developer may be experienced with a given code base.
-She would have a thorough understanding of the project, its objectives, and its implementation.
+She has a thorough understanding of the project, its objectives, and its implementation.
 She is in a position that allows her to author design rules and verify that certain rules have been followed through the project.
@@
 Such a developer may have a general familiarity with the code and its implementations, but is not able to easily or confidently author design rules or may simply wish to explore possible existing design rules.
-On her own she is not be able to produce an accurate rule, but might be able to see a rule and provide useful feedback on its correctness or relevancy.
+On her own, she is not be able to produce an accurate rule, but might be able to see a rule and provide useful feedback on its correctness or relevancy.
 Finally, a developer may be completely unfamiliar with a code base.
@@
 
- Work has already been completed with regards to the first category, and while much research has been done in code suggestion, completely automated design rule generation seems largely unexplored (see Section~\ref{relatedWorks}).
-Therefore, an algorithm developed with the second category of developers in mind forms a natural bridge between human authored design rules and completely automated rule authoring.
+Work has already been completed with regards to the first category of developers, and while much research has been done in code suggestion, completely automated design rule generation seems largely unexplored (see Section~\ref{relatedWorks}).
+Therefore, an algorithm developed with the second category of developers in mind forms a natural bridge between human-authored design rules and completely automated rule authoring.
 Consequently, we assume the developers for which we are designing our algorithm have some general familiarity with the code and can identify proper design rules if supplied with a set of rules to consider.
@@
 
-Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree of interest model to reflect developers' knowledge of code \cite{FritzEtAl2007}.
+Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree-of-interest (DOI) model to reflect developers' knowledge of code \cite{FritzEtAl2007}.
 The researchers' model was based on the total number of interactions the programmer has with an element and the recency of that interaction.
@@
 \subsubsection{Filtering information}
-\subsubsection{Identifying token}
 \subsubsection{Generating queries}
@@
 
-Some researchers developed a tool to help a person who is new to an open-source software project find relevant artifacts to a project in order to facilitate their ability to more quickly perform a given task.
-They consider all of the previously produced material, including versions of the source, the bugs, archived electronic communication, and web documents, to suggest possibly relevant sources of information to a user \cite{CubranicMurphy2003}.
+Through what is called implicit group memory, Hipikat is a client-server system that automates the mentor-like relationship that develops between developers who are new to a project and senior developers who watch over the newcomers and pass down knowledge.
+Hipikat learn from four types of artifacts and communications stored in a project's history: bug and feature descriptions, source file revisions, messages posted on developer forums, and other project documents.
+Artifacts may be queried, and the artifact database may be searched \cite{CubranicAndMurphy2003}.
 
@@
 It automatically updates its interface with correct examples and violations of design rules written in the program \cite{MehrpurEtAl2019}.
-Neither of these tools integrates information from sources outside of the code base such as cursor information or search history.
-Mylar is a tool designed for the Eclipse IDE that tries to highlight file names and code segments that are most likely to contain relevant information for a developer's current task.
-The highlighting is based off a model that depends on which elements of the code have been edited and accessed most recently \cite{KerstenMurphy2005}.
+Neither of these tools, however, integrates information from sources outside of the code base such as cursor information or search history.
+Mylar is a tool that exists within the Eclipse IDE and encodes a programmer's activity with code into a DOI model that can then be used to highlight information in a program that may be related to the task that a developer is completing.
+This model focuses on individual program elements without taking into account the possible structural relationships that may exist between program elements \cite{KerstenEtAl2005}.
 
@@
 \clearpage
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}\label{disc}
-
-\clearpage
 

### 2019-07-01 paper.tex
Add files via upload
Updated problem description; fixed some typos; placed preliminary stuff about FP algorithms and association rule mining. Comments/notes in red are notes I left to myself, but if you (Emily) want to fix those things that pertain to those notes or add to what I wrote, you are more than welcome.

@@
 As code is written and the project develops, various design decisions are made, which impact both existing and future code: ideally, as code is authored or modified, it should follow design rules used to author prior code.
-The \textit{design rules} for a project are the set of choices about the code's design and their implementation.
+A project's \textit{design rules} are the set of choices about the code's design and their implementation.
 Documentation of design rules and the rationale behind them is dependent on the developer, and when it is recorded, it is often dispersed among several disparate locations, including a formal document, comments in the code, and the developers themselves.
@@
 Finding an excessive number of non-existent rules or missing important rules would discourage developers from using the tool to document their code.
-Hence our focus is to intelligently determine which patterns in a codebase of any language are most meaningful as rules and how to find them reasonably quickly.
+Hence our focus is to intelligently and efficiently determine and interpret the patterns in a codebase that are most indicative and representative of meaningful design rules.
 
@@
 
-Association rule mining? Some brief description of our algorithm?
+\tcr{Note the following paragraph (surrounded by red brackets) is a rough outline of what our process will be; it is vague and most certainly will change: [ }Our approach to suggesting rules is threefold.
+First, we identify and record the presence of key features in the code base in a binary database that associates the features with specific sections of the code.
+Second, we use association rule mining to associate these key features together.
+Finally, we use the associated key features to construct the most likely rules, which we present to the user for acceptance or modification.
+\tcr{]}
 
+ We structure the rest of this paper as follows: In Section~\ref{probDesc}, we define our goal within the context of association rule mining, and we describe our approach given the assumptions we are making about the user.
+In Section~\ref{toolInterface}, we describe the general structure of the tool interface we would like to implement.
+Finally, in Section~\ref{relatedWorks} and Section~\ref{disc} we present related works and discuss the efficiency and limitations of our implementation.
  \clearpage
@@
 We will begin by first addressing different sources of information that are available and most useful for our purpose.
-Then, we will proceed to discuss our algorithm for design rule mining.
+Then, we will proceed to discuss our association rule mining algorithm for identifying code patterns and synthesizing design rules.
 
@@
 
-\textit{Debugger.} [Insert something later when we know what exactly we will be using about how we are using the debugger as a source of information ]
+\textit{Debugger.} [Insert something later when we know how exactly we will be using the debugger as a source of information ]
 
-\textit{Cursor location.} [Insert something later when we know what exactly we will be using about how we are using the cursor location as a source of information ]
+\textit{Cursor location.} [Insert something later when we know how exactly we will be using the cursor location as a source of information ]
 
-\textit{Search history.} [Insert something later when we know what exactly we will be using about how we are using the search history as a source of information ]
+\textit{Search history.} [Insert something later when we know how exactly we will be using the search history as a source of information ]
 
-\textit{Developer.} [Insert something later when we know what exactly we will be using about how we are using the developer as a source of information ]
+\textit{Developer.} [Insert something later when we know how exactly we will be using the developer as a source of information ]
+
+\textit{Code base.} [Insert something later when we know how exactly we will be using the code base as a source of information ]
 
@@
 
-\subsubsection{Filtering information}
+We need an efficient and compact way to represent the sundry features of a codebase and of identifying which features commonly appear together.
+The field of association rule mining is recognized for its ability to discover sets of items that co-occur with high prevalence without much previous information about the population or features \cite{AiEtAl2018}.
+Given that we are trying to associate a set of features for a codebase without any dependable knowledge about which features are most likely to be most common, association rule mining presents useful and powerful tools.
+There are several challenges that we encounter.
+First we have a large number of features, especially in comparison to the number of files in which those features are found, so our chosen algorithm must work with high dimensional data.
+Second, code bases are active documents; they are constantly changing and updating, and their features are constantly changing as well, so our algorithm must work with incremental data.
+Finally, many association rule mining algorithms are recursive, but the data structure used to compact and mine the key features can become so deep that a recursive algorithm can cause a stack overflow error, so our algorithm should be iterative.
+Therefore, we need an incremental, non-recrusive association rule miner that can efficiently analyze high dimensional data.
+In the following subsections, we begin by establishing the notation we will use for the rest of the paper; we discuss how we filter, aggregate, and update the database used with the association rule miner; we discuss the details of the algorithm we implemented and how we generate queries using the key features we association.
+Finally, we discuss how queries are selected and presented to the user.
+
+\subsubsection{Notation}
+
+In association rule mining, the database, $D$, from which the rules are mined are composed of features (columns) and transactions (rows).
+The set of features, more commonly referred to as \textit{items} are what we wish to find associations between.
+Each transaction, represents an instance of the dataset that contain certain features.
+In our case, each file is a transaction that contains several code features which we wish to associate in order to derive rules.
+Let $I=\{i_1, i_2, \ldots, i_n\}$ be the set of all $n$ features that are present in the code base that we use to identify patterns, and let $T$ be a transaction, which is a subset of $I$.
+An association rule is an inference between two subsets, $X$ and $Y$, such that $X \rightarrow Y$ and $X \cap Y = \emptyset$.
+In association rule mining, $X$ is referred to as the \textit{antecedent} and $Y$ is known as the \textit{consequent}.
+The \textit{frequency} is the number of rows that contain $X$; the \textit{support} is the fraction of all rows that contain the itemset.
+The support of $X \rightarrow Y$ is the union of $X$ and $Y$.
+The confidence of $X \rightarrow Y$ is the conditional probability of $Y$ given $X$.
+In association rule mining, an itemset is considered \textit{frequent} if its support is greater than or equal to a user-specified minimum support threshold.
+
+\subsubsection{Filtering, aggregating, and updating information}
+
+\subsubsection{Identifying code patterns}
+
 \subsubsection{Generating queries}
+
 \subsubsection{Selecting queries to present to user}
@@
 Hipikat learn from four types of artifacts and communications stored in a project's history: bug and feature descriptions, source file revisions, messages posted on developer forums, and other project documents.
-Artifacts may be queried, and the artifact database may be searched \cite{CubranicAndMurphy2003}.
+Artifacts may be queried, and the artifact database may be searched \cite{CubranicMurphy2003}.
 
@@
 Mylar is a tool that exists within the Eclipse IDE and encodes a programmer's activity with code into a DOI model that can then be used to highlight information in a program that may be related to the task that a developer is completing.
-This model focuses on individual program elements without taking into account the possible structural relationships that may exist between program elements \cite{KerstenEtAl2005}.
+This model focuses on individual program elements without taking into account the possible structural relationships that may exist between program elements \cite{KerstenMurphy2005}.
+
+\bigskip
+
+\tcr{Imagine some bridge between the two of these or maybe the following section gets shifted up to the algorithm section??}
+
+A naive approach, known as the Apriori approach, is to generate all candidate sets and then eliminate candidate sets whose support is less than the minimum support threshold.
+Depending on the number of  items, this can grow computationally prohibitive, so many authors look for ways to eliminate candidate set generation and to minimize the number of times the database needs to be scanned in order to produce frequent itemsets and association rules \cite{NarvekarSyed2015, WeiEtAl2014, EzeifeSu2002, LiEtAl2006}.
+
+\tcr{Continued discussion of FP mining; I'm holding off on inserting this into the document until we are more certain about the algorithm we wish to use, just so that we only pick the most related works.}
+
+\bigskip
 

### 2019-07-09 paper.tex
small addition

@@
 The field of association rule mining is recognized for its ability to discover sets of items that co-occur with high prevalence without much previous information about the population or features \cite{AiEtAl2018}.
-Given that we are trying to associate a set of features for a codebase without any dependable knowledge about which features are most likely to be most common, association rule mining presents useful and powerful tools.
-There are several challenges that we encounter.
+Given that we are trying to associate a set of features for a codebase without any dependable knowledge about which features are most likely to be most common, association rule mining presents a useful and powerful tool.
+However, we still encounter are challenges.
 First we have a large number of features, especially in comparison to the number of files in which those features are found, so our chosen algorithm must work with high dimensional data.
-Second, code bases are active documents; they are constantly changing and updating, and their features are constantly changing as well, so our algorithm must work with incremental data.
+Second, code bases are active documents; as the project progress, files are added, modified, and deleted, and their features may be added, modified, and deleted as well.
+Thus our algorithm must work with incremental data.
 Finally, many association rule mining algorithms are recursive, but the data structure used to compact and mine the key features can become so deep that a recursive algorithm can cause a stack overflow error, so our algorithm should be iterative.
-Therefore, we need an incremental, non-recrusive association rule miner that can efficiently analyze high dimensional data.
-In the following subsections, we begin by establishing the notation we will use for the rest of the paper; we discuss how we filter, aggregate, and update the database used with the association rule miner; we discuss the details of the algorithm we implemented and how we generate queries using the key features we association.
+Therefore, we need an incremental, non-recursive association rule miner that can efficiently analyze high dimensional data.
+In the following subsections, we begin by establishing the notation we will use for the rest of the paper; we discuss how we filter, aggregate, and update the database used with the association rule miner; we discuss the details of the algorithm we implemented and how we generate queries using the key features we associate.
 Finally, we discuss how queries are selected and presented to the user.
+
+// Aren't the first and third challenges related? Should they be explained together?
+
+Node-FPGrowth is a Node.js module implemented by Alexis Facques and accessible online through the npm registry. (citation) Explanation of fpgrowth here
 
@@
 \subsubsection{Filtering, aggregating, and updating information}
+Explanation of createData.py
 

### 2019-07-31 paper.tex
Add files via upload

--- 2019-06-24 paper.tex
@@
 \usepackage{pbox}
+
+\usepackage{subfig}
 
@@
 
+\setcounter{tocdepth}{4}
+\setcounter{secnumdepth}{4}
+
 \usepackage{bibentry}
 
+\usepackage{listings}
+
+\definecolor{lightgray}{gray}{0.9}
+
+\lstset{
+    showstringspaces=false,
+    basicstyle=\ttfamily,
+    keywordstyle=\color{blue},
+    commentstyle=\color[grey]{0.6},
+    stringstyle=\color[RGB]{255,150,75}
+}
+
+\newcommand{\inlinecode}[2]{\colorbox{lightgray}{\lstinline[language=#1]$#2$}}
+
 \title{S19: REU Research Document}
-\author{Emily Slaughter, Gennie Mansi}
+\author{Emily Slaughter, Gennie Mansi }
 
@@
 
+The term design rules refers to the choices about the design of a project and how those choices are implemented.
+Design rules are integral in maintaining project coherency and forwards and backwards compatibility.
+Documentation is critical to preserving information about design rules.
+However, most documentation is not updated frequently, and only individual developers know critical pieces of information.
+We developed an algorithm that can represent the information contained in a code base and automatically suggest likely design rules.
+Our results demonstrate that our algorithm can successfully represent and identify significant design rules, and has the potential to be used to automatically generate documentation for a project.
+
 \clearpage
@@
 
-Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed teams.
-As code is written and the project develops, various design decisions are made, which impact both existing and future code: ideally, as code is authored or modified, it should follow design rules used to author prior code.
-The \textit{design rules} for a project are the set of choices about the code's design and their implementation.
-Documentation of design rules and the rationale behind them is dependent on the developer, and when it is recorded, it is often dispersed among several disparate locations, including a formal document, comments in the code, and the developers themselves.
-However, documentation is often not written, read, or updated, and coworkers are not always a reliable resource \cite{KoEtAl2007}.
-Lack of documentation ultimately causes newcomers to a project to depend largely on the code rather than explicit, written documentation to understand such project-specific design rules.
+Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed developers.
+As code is written and a project develops, various design decisions are made, which impact both existing and future code.
+Documentation of design decisions and the rationale behind those decisions is dependent on the developer and is often recorded or dispersed between several disparate locations, including a formal document, comments in the code, and the developers themselves.
+However, documentation is often not written, read, or updated, causing developers to depend largely on the code and other sources of information rather than explicit, written documentation.
 
-A tool that mines and recommends design rules has the potential to facilitate active documentation of code, allowing developers to efficiently and accurately apply and maintain a unified set of design rules.
-There are an exponential number of patterns that could be found in a given code base, and some rules have greater relevance than others.
-Finding an excessive number of non-existent rules or missing important rules would discourage developers from using the tool to document their code.
-Hence our focus is to intelligently determine which patterns in a codebase of any language are most meaningful as rules and how to find them reasonably quickly.
+Ideally, as code is authored or modified, it should follow design rules that were previously used to author code.
+The \textit{design rules} for a project are the set of choices about the code's design and how those choices are implemented.
+Several sources of information, including search history, cursor location, event logs, debugger information, and the code itself can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest.
+Some information about design rules may only be recorded in the memories of co-workers, and thus access to this kind of information is also critical for developers trying to understand and use existing code.
 
-Several sources of information in addition to the code itself, including search history, cursor location, event logs, and debugger information can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest.
-We explore how this information from outside of the code base can be combined with the code base itself to inform what patterns are identified.
+Mixed human-AI authoring of code patterns can greatly assist developers to efficiently and accurately develop and maintain a unified set of rules.
+There are an infinite number of patterns that could be found in a given code base, and an even larger diversity of representations for those patterns; therefore, the crux of the problem lies in determining how to represent the information contained in the code base and in identifying the patterns using the chosen representation.
+Hence our focus is on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.
+
+We explore how information from outside of the code base could be used to inform what patterns are identified.
+We seek to develop a tool that combines both automatic and manual rule-authoring capabilities.
+It should also automatically provide live updates with examples and violations of authored design rules.
 Ultimately, such a tool will greatly increase the amount of up-to-date documentation available to developers.
-We seek to develop a tool that automates the manual rule-authoring capabilities of ActiveDocumentation \cite{MehrpurEtAl2019} and preserves its live-update features.
 
-Association rule mining? Some brief description of our algorithm?
+The rest of the paper is organized as follows.
+Section~\ref{methods} contains assumptions that are made about developers, a discussion of the different sources of information about design rules that are available, and a description of our algorithm.
+We discuss our three different approaches to representing the components of design rules in Section~\ref{algm_attrApproaches}.
+Section~\ref{results} contains a description of the results for our algorithm, followed by a description of the tool interface in Section~\ref{toolInterface}.
+Finally, we discuss the short comings of our algorithm and related in works in Sections~\ref{relatedWorks} and Sections~\ref{disc}, respectively.
 
@@
 First, a developer may be experienced with a given code base.
-She has a thorough understanding of the project, its objectives, and its implementation.
-She is in a position that allows her to author design rules and verify that certain rules have been followed through the project.
+She would have a thorough understanding of the project, its objectives, and its implementation.
+She is in a position that allows her to author design rules and verify that certain rules have been followed throughout the project.
 Second, a developer may be partially knowledgable about a project and its implementation.
 Such a developer may have a general familiarity with the code and its implementations, but is not able to easily or confidently author design rules or may simply wish to explore possible existing design rules.
-On her own, she is not be able to produce an accurate rule, but might be able to see a rule and provide useful feedback on its correctness or relevancy.
+On her own she is not be able to produce an accurate rule, but she might be able to see a rule and provide useful feedback on its correctness or relevancy.
 Finally, a developer may be completely unfamiliar with a code base.
@@
 
-Work has already been completed with regards to the first category of developers, and while much research has been done in code suggestion, completely automated design rule generation seems largely unexplored (see Section~\ref{relatedWorks}).
-Therefore, an algorithm developed with the second category of developers in mind forms a natural bridge between human-authored design rules and completely automated rule authoring.
+ Work has already been completed with regards to the first category, and while much research has been done in code suggestion, completely automated design rule generation seems largely unexplored (see Section~\ref{relatedWorks}).
+Therefore, an algorithm developed with the second category of developers in mind forms a natural bridge between human authored design rules and completely automated rule authoring.
 Consequently, we assume the developers for which we are designing our algorithm have some general familiarity with the code and can identify proper design rules if supplied with a set of rules to consider.
@@
 	Part of knowing which sources are most useful for deriving information about design rules is understanding where developers themselves look for information about a project and what kinds of information are useful to programmers.
-
-\subsection{Possible sources}
 
@@
 Additionally, they identify knowledge about design and program behavior as the type of information that is most often deferred since unavailable coworkers are often the only source of knowledge.
-Developers sought out coworkers most often when there are information needs with regards to code design.
+Developers sought out coworkers most often when there were information needs with regards to code design.
 Other questions to coworkers centered around following the team's conventions.
@@
 
-Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree-of-interest (DOI) model to reflect developers' knowledge of code \cite{FritzEtAl2007}.
+Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree of interest model to reflect developers' knowledge of code \cite{FritzEtAl2007}.
 The researchers' model was based on the total number of interactions the programmer has with an element and the recency of that interaction.
@@
 
-Based off of  these findings, we identified the debugger (?), code base, cursor location and search histories, and the developer herself as the most pertinent and accessible sources of information for our algorithm.
+Based off of  these findings, we can conclude that there are a variety of pertinent and accessible sources of information for our algorithm, including the debugger, code base, cursor location and search histories, and the developer herself.
+However, we focus on trying to find rules using only the code base and direct feedback from the developer.
+The reason for this decision is that the code base and direct feedback are the only two sources of information that we are guaranteed.
+Future iterations of this algorithm may also use these other sources of information to generate design rules.
 
-\textit{Debugger.} [Insert something later when we know what exactly we will be using about how we are using the debugger as a source of information ]
+\subsection{Representing the code base and design rules}
+Our representation of the features in the code base ultimately impacts the way that we identify design rules.
+Ideally, we would output information only about the most critical features of the code base that can lead us to the most likely design rules.
+However, the code base contains a lot of information and there are many ways of representing that information.
+Additionally, there are scalability concerns since code bases can easily have over a quarter million lines of code.
+Ultimately, our representation of the features of the code base is linked to the way that design rules can be represented.
 
-\textit{Cursor location.} [Insert something later when we know what exactly we will be using about how we are using the cursor location as a source of information ]
+Design rules can be represented as ``IF/THEN" statements where \textit{IF} some quality is true about a section of code \textit{THEN} some condition is applied.
+We represent different features of the code using \textit{attributes}.
+An attribute is a way of representing some feature(s) of the code.
+Thus, we can decompose design rules into a set of attributes.
+The ability to group attributes into ``IF" attributes and ``THEN" attributes would enable us to generate design rules.
+Our goal then is to associate different attributes about the code base, so we can synthesize them to create design rules.
 
-\textit{Search history.} [Insert something later when we know what exactly we will be using about how we are using the search history as a source of information ]
+The challenge then is what kinds of attributes to generate (that is, what kinds of representations for the code to use), since there are many different ways to represent the features of a code base (see Figure~\ref{fig:attrEx}).
+Consequently, there are many ways to represent a design rule (Figure~\ref{fig:drEx}).
 
-\textit{Developer.} [Insert something later when we know what exactly we will be using about how we are using the developer as a source of information ]
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{attributeEx.png}
+  \caption{There are many different attributes that can be created that represent different features of the code in different ways.}
+  \label{fig:attrEx}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{designRuleEx.png}
+  \caption{Notice that from the same segment of code, we have many different ways of representing the corresponding design rule.}
+  \label{fig:drEx}
+\end{figure}
 
@@
 
-\subsubsection{Filtering information}
-\subsubsection{Generating queries}
+\subsubsection{Outputting the attributes}\label{algm_attrApproaches}
+
+We approached outputting attributes in three different ways, all of which we present in Section~\ref{algm} and analyze in Section~\ref{results}.
+Figure~\ref{fig:attrFunction}, ~\ref{fig:attrConstructor}, ~\ref{fig:attrField}, and ~\ref{fig:attrClass} contain a summary of the different kinds of attributes output by each of these algorithms.
+For all four of these figures, yellow dots represent Approach 1, green dots represent Approach 2, and orange dots represent Approach 3.
+
+	\paragraph{Approach 1}
+
+	The basic idea in this approach is that we would have a set of reserved item IDs corresponding to “default” attributes that we know we always have a chance of finding.
+For example, there is always the chance that there is a public class; thus, there is a reserved item ID corresponding to an attribute titled “is a public class”.
+We also output attributes that are specialized to the code base from which they are derived, such as annotations that are on classes and what classes are involved in an inheritance structure.
+Each line output to the database represented the set of attributes belonging to a different class in the code base.
+
+	\paragraph{Approach 2}
+
+	The second approach entailed generating several databases that could be further mined for more detailed information.
+The logic behind this approach is that it might be easier to output more specific attributes for different subsets of the data that are related, and thus find more specific and interesting rules.
+Each starting database would have rows composed of different subsets of the data that are related.
+For example, one database might contain more specific attributes related to subclasses, with each row in the database representing a different subclass.
+Other output databases may have rows composed of the different functions in a class, and another would have rows representing different subclasses.
+Once these databases are generated, association rules would be derived from them.
+Based off the association rules that are created, a second more detailed database might be created in order to mine more specific information about the rule.
+For example, the database with rows made from distinct functions might generate a rule that says “IF there is a function that returns the call from a constructor
+THEN it needs to return a specific type $<$type name$>$.” The second database created would be composed of rows all of which are functions that return the call from a constructor and return the specific type.
+Attributes for the derived database could include more specific characteristics about the constructor, such as the parameters required by the constructor and the type of object created by the constructor.
+Then, if needed, a tertiary, more specific database could be output with even more specific attributes.
+
+	\paragraph{Approach 3}
+
+	Our third approach entails outputting more detailed attributes about subsets of the code base and analyzing the attributes found in the subsets for design rules.
+For each subset of the code base, we have a \textit{focus} class from which a set of global attributes is created; any class in the subset that is not the focus class is a \textit{peripheral} class.
+Only the attributes found in both the focus class and peripheral classes are output.
+The main advantage to outputting the attributes in classes this way is that it is more scalable.
+Since the set of global attributes is compiled only of the attributes of a single class, a greater number of attributes can be output without significantly decreasing efficiency or scalability.
+
+	The attributes that are output are a mix of more and less detailed attributes about subsets of the different classes in the code base.
+Many of the same attributes are output by both this approach and Approach 1.
+However, in this approach we also output more specific attributes that contain information about multiple features.
+Attributes specifically include annotations on classes, functions, and fields complete with the annotation name and arguments, constructors storing all of the values passed as arguments in member variables, constructors having empty bodies or non-empty bodies, the return types of functions.
+
+\begin{figure}
+\centering
+\parbox{8 cm}{
+\includegraphics[width=\linewidth]{attributeFunctions.png}
+\caption{A comparison of the attributes regarding functions produced by Approach 1, 2, and 3.}
+\label{fig:attrFunction}}
+\qquad
+\begin{minipage}{7.5 cm}
+\includegraphics[width=\linewidth]{attributeConstructors.png}
+\caption{A comparison of the attributes regarding constructors produced by Approach 1, 2, and 3.}
+\label{fig:attrConstructor}
+\end{minipage}
+\end{figure}
+
+\makebox[\textwidth]{attributeFunctions.png}
+
+\begin{figure}
+\centering
+\parbox{7.5 cm}{
+\includegraphics[width=\linewidth]{attributeFields.png}
+\caption{A comparison of the attributes regarding functions produced by Approach 1, 2, and 3.}
+\label{fig:attrField}}
+\qquad
+\begin{minipage}{8 cm}
+\includegraphics[width=\linewidth]{attributeClass.png}
+\caption{A comparison of the attributes regarding constructors produced by Approach 1, 2, and 3.}
+\label{fig:attrClass}
+\end{minipage}
+\end{figure}
+
+\subsubsection{Associating attributes}
+	We chose the Frequent-Pattern (FP) Growth Algorithm, which is an algorithm frequently used in association rule mining (ARM).
+ARM seeks to mine databases for patterns of items that frequently occur together.
+It is often used in market basket analysis to see what products are often purchased simultaneously.
+FP Growth is a type of association rule mining algorithm that efficiently finds frequent itemsets (FIs) by storing their patterns in a tree data structure.
+Advantages of the FP Growth algorithm include:
+	\begin{itemize}
+		\item It’s designed to find hidden patterns among items.
+		\item Its scalability and relative efficiency.
+		\item Various implementations that deal with sparse data already exist.
+	\end{itemize}
+In our case, the items in the FIs output by the algorithm are groups of attributes that frequently appear together in the code base.
+
+There are two notions of frequency that are used in FP-Growth and other ARM techniques:
+	\begin{enumerate}
+		\item Support - the joint probability of two or more items.
+		\item Confidence - the conditional probability of two or more items.
+	\end{enumerate} 
+Both are typically expressed as percentages ranging from 0-100\%, and are used to produce FIs that occur with a particular frequency.
+The support and frequency are used to fine tune the algorithm and varying them can result in finding different FIs.
+
+\subsubsection{Generating candidate design rules}
+
+Once the FIs have been produced an extension of the algorithm produces association rules.
+Items in an association rule are either in the antecedent (``IF") portion of the rule or the consequent (``THEN") portion of the rule.
+Rules are interpreted, ``IF (\textit{insert antecedent}) THEN also (\textit{antecedents}) tend to be present".
+We use the association rules produced from the algorithm as our candidate design rules to present to the developer.
+
 \subsubsection{Selecting queries to present to user}
 
+\tcr{[Work in progress]}
+
 \clearpage
+
+%%%%%%%%%%%%%%%%%%%
+\section{Results} \label{results}
+In order to assess our success in identifying “interesting” rules, we used a set of sample design rules written for a java-based project called CrowdCode.
+CrowdCode is a program designed to help groups of developers delegate and keep track of tasks for large coding projects and software.
+For each approach discussed in Section~\ref{algm}, we analyze how well we could reproduce the sample design rules for CrowdCode as well as scalability concerns.
+
+	\subsection{Approach 1}
+	This approach was not successful even when used with lower support (20-40\%).
+The general problem was that associations produced from this database were uninteresting and obvious.
+For example, many of the rules produced were rules such as, “IF it is a public class THEN it has a public function” or “IF it is a class with annotation @$<$class name$>$ THEN it is a class that has an annotation”.
+
+The reason such association rules were output is due to the fact that all the attributes were fairly general, and many default attributes overlapped with more specific attributes, such as the above example with annotations.
+These overlapping attributes always occurred together, and thus most of the rules FP-Growth produced were made of overlapping attributes.
+Hence, more interesting rules could not be discovered.
+
+	\subsection{Approach 2}
+	The main prohibiting factor in this approach, is the total number of tables created and the total number of times the code would need to be traversed to create all of the tables.
+Consequently, we found this approach to be impractical, and did not seek to pursue this approach further.
+
+	\subsection{Approach 3}
+
+	We explored 6 different groups of files to test if we could find the attributes of interest.
+The focus class was chosen as the class with the largest file size that was not the parent class if there was an inheritance structure.
+We present the groups of classes that were successfully used to identify one of our target design rules.
+Under each group of classes, we list the rules that we found along with an explanation.
+A discussion of what rules could not be discovered and why follows this portion.
+Supplementary material contains the output for all six groupings.
+
+	\subsubsection{Command classes}
+		This group included classes that extended the Command class and the Command class itself. The focus class for this group was \inlinecode{Java}{QuestioningCommand.java}.
+
+		\paragraph {Rules found}
+
+			\subparagraph{Commands must implement execute} IF a class is a subclass of Command THEN it must implement execute.
+
+			The attributes of interest that are generated here are (1) class extends Command, (2) has public function execute(), (3) has void function execute().
+We output both these attributes, so we should be able to find them together in frequent itemsets.
+We used support 60\% and confidence 80\% for all our tests.
+		\begin{itemize}
+			\item (1) and (2) were found together in approximately 22\% of all FIs.
+			\item (1) and (3) were found together in approximately 12\% of all FIs.
+			\item (1), (2), and (3) were found together in approximately 6\% of all FIs.				\item (2) and (3) were found together in approximately 12.5\% of all FIs. 
+		\end{itemize}
+
+			\subparagraph{Commands should persist all data they are given.} IF a constructor is for a subclass of Command THEN it should store each parameter given.
+
+			The attributes of interest that we represent are (1) class extends command and (2) constructor stores each parameter given.
+We used support 60\% and confidence 80\% for all our tests.
+Both attributes were found in about 24\% of all FIs.
+
+	\subsubsection{Classes and subclasses that extend DTO }
+		This group included classes that extended the DTO class and the subclasses of the classes that extended the DTO class. The focus class for this group was \inlinecode{Java}{FunctionInFirebase.java}.
+
+		\paragraph {Rules found}
+
+		\subparagraph{DTOs must have a zero-argument constructor.} IF a class is a DTO object THEN it needs to have a zero-argument constructor with an empty body.
+
+		The attributes of interest are (1) class extends DTO, (2) class has zero-args constructor, and (3) class has empty body.
+With 60\% support and 80\% confidence, these three attributes were found in 6.5\% of the FIs.
+
+	\subsubsection{Classes, subclasses, and sub-subclasses that extend DTO}
+		This group included classes that extended the DTO class and the subclasses and sub-subclasses of the classes that extended the DTO class.
+The focus class for this group was  \inlinecode{Java}{FunctionInFirebase.java}.
+
+		\paragraph {Rules found}
+
+		\subparagraph{DTOs must have a zero-argument constructor.} IF a class is a DTO object THEN it needs to have a zero-argument constructor with an empty body.
+
+		The attributes of interest are (1) class extends DTO, (2) class has zero-args constructor, and (3) class has empty body.
+With 60\% support and 80\% confidence, these three attributes were found in 5.1\% of the FIs.
+
+	\subsubsection{@Entity classes}
+		This group included all the classes that had the @Enitty notation placed directly above them. The focus class for this group was \inlinecode{Java}{Project.java}.
+		\paragraph {Rules found}
+
+		\subparagraph{@Entity classes must have an @id field.} IF a class has an @Entity annotation THEN it must have a field annotated with @Id.
+
+		The attributes of interest are (1) class has @Entity notation and (2) member field has annotation @id.
+With 50\% support and 80\% confidence, approximately 22\% of all FIs generated by the FP growth algorithm contained these two attributes.
+
+		\subparagraph{Subclasses of @Entity classes must be indexed.} IF a class is a subclass of an @Entity class THEN it needs to be indexed ('index=true').
+\tcr{[I couldn't find exact numbers on what percentages were output for these groupings.]}
+
+		\subparagraph{@Entity classes must have a zero-argument constructor.} IF a class is an entity THEN it needs to have a zero-argument constructor.
+
+		The attributes of interest are (1) has @Entity annotation and (2) class has zero-args constructor.
+With 60\% support and 80\% confidence, approximately 20\% of the FIs generated by the FP growth algorithm contained these two attributes; as a side note, if support was lowered to 50\%, then approximately 23\% of the FIs generated contained both attributes.
+
+	\subsubsection{Artifact classes }
+		This group included all the classes that extended the Artifact class. The focus class for this group was \inlinecode{Java}{Function.java}.
+
+		\paragraph {Rules found}
+
+		\subparagraph{Artifacts should be marked as a data region with an @Entity annotation}.  IF an object is an artifact subclass THEN it needs to be an entity.
+
+		In this case, the attributes of interest are ``extends Artifact” and ``class has @Entity annotation”.
+With 60\% support and 80\% confidence, just under half of all FIs generated by the FP growth algorithm contained these two attributes.
+
+	\subsubsection{Rules not found}
+
+		\subparagraph{Creating an Artifact should be indirected through a Command.} IF a new Artifact is to be created THEN its constructor should be invoked only by its corresponding Command class.
+
+		We are not able to generate this rule because we do not create attributes that would allow us to find this rule.
+We do generate an attribute that would indicate that an Artifact object is created, and attributes indicating that there were functions in which the respective Artifact class constructor was called, but there isn’t a way to communicate the idea of invoking the Artifact constructor only with the corresponding Command class.
+
+		\subparagraph{Communication between artifacts should be indirected through a Command.} IF an Artifact needs to communicate with another artifact THEN it should create a Command describing the desired action to be performed.
+
+        We also can’t represent this rule with our current set of attributes for similar reasons as the previous rule.
+The difficult part of this rule is that we output attributes in the form “function foo() calls ECommand constructor” or “function foo() calls FCommand constructor”, which will not get associated together in a group because the names of the classes are different.
+Further, the program uses a single focus class to generate a set of global attributes that are searched for in related classes.
+Consequently, we pass the function an xml file that contains only the file for the focus class, which means we cannot find out what the parent of the current class extends since the file only contains the information for the focus class.
+
+        		\subparagraph{All Microtask commands must be handled by Command subclasses.} IF a method is a static method on Command THEN it should implement its behavior by constructing a new Command subclass instance.
+
+		Again, while we can/do output attributes for the “IF” portion of this rule, we cannot output attributes for the “THEN” portion of this rule because we only create attributes from a single input class, and therefore cannot create an attribute that represents this information.
+
+		\subparagraph{Commands should not be publicly visible.} IF a class is a subclass of Command THEN it should not be public.
+
+		While we do output visibility specifiers and inheritance information, we cannot output this rule because we only output visibility specifiers for the focus class.
+Therefore, if the focus class is public, we will output “class is public” but we will not output any attributes about private or protected classes.
+One solution is to include default attributes such as “is private class” and “is protected class” in the global set of attributes.
+Theoretically, we can find implement our attribute outputting algorithm so that this information can be output.
+However, our current method does not allow us to output attributes that could be used to represent this rule.
+
+		\subparagraph{@Entity classes must be registered in the CrowdServlet class.} IF a class is an Entity class or subclass THEN it must be registered in CrowdServlet by ObjectifyService.
+
+		Again, we cannot output this rule because of the kinds of attributes that are output by our approach.
+In order for a class to be ``registered", a function call to the register function must be made by an ObjectifyService object with the class to be registered as the argument.
+The difficulty comes in trying to track that a function call has been made by a particular class.
+Without any prior information, it is difficult to recognize which attributes should be made about which function calls in which classes.
+Since there are thousands and even hundreds of thousands of functions calls in a given code base, the scalability of trying to output information about every function call makes representing this information in attributes rather intractable.
+
+		\subparagraph{Save() calls should always be committed immediately.} IF the save method is called THEN the now() method must be followed immediately.
+
+		A similar problem to the previous rule exists to this one.
+Any number of attributes could be generated with all the possible pattern combinations of ordered function calls; however, this would cause an explosion of attributes that would likely render outputting attributes and finding associations intractable.
+One possible way of trying to find this rule might use a pattern finding technique from association rule mining.
+The database such a technique might be trained on may be in which each row represents a different function, and the attributes for each function would represent the function calls made with in that section of the code.
+A sequential pattern mining algorithm would look for the patterns in this database.
 
@@
 
-Through what is called implicit group memory, Hipikat is a client-server system that automates the mentor-like relationship that develops between developers who are new to a project and senior developers who watch over the newcomers and pass down knowledge.
-Hipikat learn from four types of artifacts and communications stored in a project's history: bug and feature descriptions, source file revisions, messages posted on developer forums, and other project documents.
-Artifacts may be queried, and the artifact database may be searched \cite{CubranicAndMurphy2003}.
+Some researchers developed a tool to help a person who is new to an open-source software project find relevant artifacts to a project in order to facilitate their ability to more quickly perform a given task.
+They consider all of the previously produced material, including versions of the source, the bugs, archived electronic communication, and web documents, to suggest possibly relevant sources of information to a user \cite{CubranicMurphy2003}.
 
@@
 It automatically updates its interface with correct examples and violations of design rules written in the program \cite{MehrpurEtAl2019}.
-Neither of these tools, however, integrates information from sources outside of the code base such as cursor information or search history.
-Mylar is a tool that exists within the Eclipse IDE and encodes a programmer's activity with code into a DOI model that can then be used to highlight information in a program that may be related to the task that a developer is completing.
-This model focuses on individual program elements without taking into account the possible structural relationships that may exist between program elements \cite{KerstenEtAl2005}.
+Neither of these tools integrates information from sources outside of the code base such as cursor information or search history.
+Mylar is a tool designed for the Eclipse IDE that tries to highlight file names and code segments that are most likely to contain relevant information for a developer's current task.
+The highlighting is based off a model that depends on which elements of the code have been edited and accessed most recently \cite{KerstenMurphy2005}.
 
@@
 %%%%%%%%%%%%%%%%%%%
-\section{Discussion}\label{disc}
 
-It might be helpful to adapt our tool to be able to work with team environments.
+\section{Discussion and Conclusion}\label{disc}
 
-I don't really feel like discussing things any more.
-Why is this the only part that is called the discussion?
-I mean, what has been the rest of everything that has been written?
-Or did you just skip here?
-Is that why it has been called ``discussion"?
+Mixed human-AI authoring of documentation has great potential for increasing and maintaining up-to-date documentation about code bases.
+In this paper, we present three different approaches for outputting attributes about a project code base.
+The results show that using the third approach we can have a flexible representation of  many design rules that we might wish to find in a code base.
+They also show that there seems to be a tractable and fast way of analyzing code to detect design rules.
+
+There are several rules kinds of attributes that we cannot represent, and, thus, we cannot find design rules that include those attributes.
+Attributes we still cannot represent are ones that include tracking sequential function calls and constructor calls across and within broad categories classes.
+Outputting these attributes usually present tractability problems and may require a different representation and algorithm in order to be detected.
+
+Another idea that needs further development and may be of use in resolving tractability and scalability challenges is the idea of \textit{interestingness}.
+Some attributes may be of more interest than others, and there is potential to include information from the IDE, previous documentation, and the developer in order to prioritize attributes or candidate design rules that are generated.
+
+While prior work has been conducted with code suggestion and degree of interest models, we believe the area of mixed human-AI documentation still has much room for improvement and study in order to more accurately and more flexibly detect the design rules used in a code base.
 

### 2019-08-02 paper.tex
Add files via upload

@@
 \pdfminorversion 3
-\usepackage{pbox}
 
 \usepackage{subfig}
+
+\usepackage{float}
+\usepackage{siunitx}
+\usepackage{soul}
+\usepackage{graphicx,caption}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage{xcolor,colortbl}
+\usepackage{longtable}
 
@@
 
-The term design rules refers to the choices about the design of a project and how those choices are implemented.
-Design rules are integral in maintaining project coherency and forwards and backwards compatibility.
-Documentation is critical to preserving information about design rules.
-However, most documentation is not updated frequently, and only individual developers know critical pieces of information.
+Documentation is critical to preserving information about the choices about the design of a project and how those choices are implemented.
+However, most documentation is not updated frequently, and often only individual developers know critical pieces of information, which are integral in maintaining project coherency and forwards and backwards compatibility.
 We developed an algorithm that can represent the information contained in a code base and automatically suggest likely design rules.
@@
 
-	\subsubsection{Command classes}
-		This group included classes that extended the Command class and the Command class itself. The focus class for this group was \inlinecode{Java}{QuestioningCommand.java}.
+	We used support 60\% for all our tests, except for the test used to generate the rule ``IF a class has an @Entity annotation THEN it must have a field annotated with @Id"; a support of 50\% was used.
+Lowered support was used to restrict the number of FI's produced by the algorithm.
+Although confidence is used in many ARM techniques, it is not used in generating FI's; thus, we did not have to specify a confidence level for the algorithm.
 
-		\paragraph {Rules found}
+\definecolor{yellow}{rgb}{1,1,0.6}
+\newcommand{\textcoloryellow}{\cellcolor{yellow}}  %{0.9}
 
-			\subparagraph{Commands must implement execute} IF a class is a subclass of Command THEN it must implement execute.
+\begin{table}[H]
+\centering
+\begin{tabular}{| >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+\hline
+\multicolumn{3}{|l|}{\textcoloryellow{\textbf{Command classes}}} \\\hline
+\multicolumn{3}{|l|}{Focus class: QuestioningCommand.java} \\\hline
+\multicolumn{3}{|l|}{Peripheral classes: Command class and classes that extend Command} \\\hline
+Rule & Attributes & \% FI that contain \\\hline
+\end{tabular}
 
-			The attributes of interest that are generated here are (1) class extends Command, (2) has public function execute(), (3) has void function execute().
-We output both these attributes, so we should be able to find them together in frequent itemsets.
-We used support 60\% and confidence 80\% for all our tests.
-		\begin{itemize}
-			\item (1) and (2) were found together in approximately 22\% of all FIs.
-			\item (1) and (3) were found together in approximately 12\% of all FIs.
-			\item (1), (2), and (3) were found together in approximately 6\% of all FIs.				\item (2) and (3) were found together in approximately 12.5\% of all FIs. 
-		\end{itemize}
+\begin{tabular}{| >{\arraybackslash}m{6.5cm} | >{\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+IF a class is a subclass of Command THEN it must implement execute. & (1) class extends Command \newline (2) has public function execute() \newline (3) has void function execute() & 6\%\\\hline
+IF a constructor is for a subclass of Command THEN it should store each parameter given. & (1) class extends command \newline (2) constructor stores each parameter given & 24\%\\\hline
+\end{tabular}
 
-			\subparagraph{Commands should persist all data they are given.} IF a constructor is for a subclass of Command THEN it should store each parameter given.
+\begin{tabular}{| >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+\multicolumn{3}{|l|}{\textcoloryellow{\textbf{DTO classes and subclasses}}} \\\hline
+\multicolumn{3}{|l|}{Focus class: FunctionInFirebase.java} \\\hline
+\multicolumn{3}{|l|}{Peripheral classes: classes that extend DTO and subclasses of classes that extend DTO} \\\hline
+Rule & Attributes & \% FI that contain \\\hline
+\end{tabular}
 
-			The attributes of interest that we represent are (1) class extends command and (2) constructor stores each parameter given.
-We used support 60\% and confidence 80\% for all our tests.
-Both attributes were found in about 24\% of all FIs.
+\begin{tabular}{| >{\arraybackslash}m{6.5cm} | >{\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+IF a class is a DTO object THEN it needs to have a zero-argument constructor with an empty body.
+& (1) class extends DTO \newline (2) class has zero-args constructor \newline (3) class has empty body & 6.5\%\\\hline
+IF a class is a DTO object THEN it needs to have a zero-argument constructor with an empty body.
+& (1) class extends DTO \newline (2) class has zero-args constructor \newline (3) class has empty body & 5.1\%\\\hline
+\end{tabular}
 
-	\subsubsection{Classes and subclasses that extend DTO }
-		This group included classes that extended the DTO class and the subclasses of the classes that extended the DTO class. The focus class for this group was \inlinecode{Java}{FunctionInFirebase.java}.
+\begin{tabular}{| >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+\multicolumn{3}{|l|}{\textcoloryellow{\textbf{@Entity classes}}} \\\hline
+\multicolumn{3}{|l|}{Focus class: Project.java} \\\hline
+\multicolumn{3}{|l|}{Peripheral classes: classes that have the @Entity annotation placed directly above them} \\\hline
+Rule & Attributes & \% FI that contain \\\hline
+\end{tabular}
 
-		\paragraph {Rules found}
+\begin{tabular}{| >{\arraybackslash}m{6.5cm} | >{\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+IF a class has an @Entity annotation THEN it must have a field annotated with @Id. & (1) class has @Entity annotation \newline (2) member field has annotation @id & 22\%\\\hline
+IF a class is a subclass of an @Entity class THEN it needs to be indexed ('index=true'). & (1) class has @Subclass notation with index = true & 48.8\% \\ \hline
+IF a class is an entity THEN it needs to have a zero-argument constructor. & (1) has @Entity annotation \newline (2) class has zero-args constructor & 20\%\\\hline
+\end{tabular}
 
-		\subparagraph{DTOs must have a zero-argument constructor.} IF a class is a DTO object THEN it needs to have a zero-argument constructor with an empty body.
+\begin{tabular}{| >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+\multicolumn{3}{|l|}{\textcoloryellow{\textbf{Artifact classes}}} \\\hline
+\multicolumn{3}{|l|}{Focus class: Function.java} \\\hline
+\multicolumn{3}{|l|}{Peripheral classes: classes that extend Artifact class} \\\hline
+Rule & Attributes & \% FI that contain \\\hline
+\end{tabular}
 
-		The attributes of interest are (1) class extends DTO, (2) class has zero-args constructor, and (3) class has empty body.
-With 60\% support and 80\% confidence, these three attributes were found in 6.5\% of the FIs.
+\begin{tabular}{| >{\arraybackslash}m{6.5cm} | >{\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
+IF an object is an artifact subclass THEN it needs to be an entity. & (1) extends Artifact \newline (2) class has @Entity annotation & 49.8\% \\\hline
+\end{tabular}
 
-	\subsubsection{Classes, subclasses, and sub-subclasses that extend DTO}
-		This group included classes that extended the DTO class and the subclasses and sub-subclasses of the classes that extended the DTO class.
-The focus class for this group was  \inlinecode{Java}{FunctionInFirebase.java}.
+\caption{This table contains rules that were found, their decompositions as target attributes, and the percentages of frequent itemsets containing the target attributes.}
+\end{table}
 
-		\paragraph {Rules found}
+\begin{table}[H]
+\centering
+\begin{tabular}{| >{\centering\arraybackslash}m{5.5cm} | >{\centering\arraybackslash}m{4.5cm} | >{\centering\arraybackslash}m{5.5cm} |}
+\hline
+Rule & Achievable & Challenge \\ \hline
+\end{tabular}
 
-		\subparagraph{DTOs must have a zero-argument constructor.} IF a class is a DTO object THEN it needs to have a zero-argument constructor with an empty body.
+Each of these rules could be represented using the attributes that we encoded from the CrowdCode database, and we were able to find these attributes in the FI's generated using the FP Growth algorithm.
+Rules that are found most often (had the largest percentage found in the FI's that are generated) tend to be rules in which the total number of classes in the group was moderately large, and the attributes shared between different classes overlaps but still vary moderately.
 
-		The attributes of interest are (1) class extends DTO, (2) class has zero-args constructor, and (3) class has empty body.
-With 60\% support and 80\% confidence, these three attributes were found in 5.1\% of the FIs.
+Furthermore, we found that while a great number of attributes was often generated by the algorithm, the number of those attributes found in the peripheral classes and output to the database was significantly less.
+Usually, over a hundred attributes would be included in the global list but about 20 different attributes would be found in the peripheral classes.
+In one case, over eight hundred total attributes were found in the focus class, but it shared only about 30 attributes with its peripheral classes.
+Thus, many FI's produced were fairly similar, differing in only a few attributes.
 
-	\subsubsection{@Entity classes}
-		This group included all the classes that had the @Enitty notation placed directly above them. The focus class for this group was \inlinecode{Java}{Project.java}.
-		\paragraph {Rules found}
+\begin{tabular}{| >{\arraybackslash}m{5.5cm} | >{\arraybackslash}m{4.5cm} | >{\arraybackslash}m{5.5cm} |}
+IF a new Artifact is to be created THEN its constructor should be invoked only by its corresponding Command class.
+& "Artifact is to be created" (i.e., call to constructor of Artifact) & There is no current way to communicate the idea of a corresponding class.
+\\ \hline
+IF an Artifact needs to communicate with another artifact THEN it should create a Command describing the desired action to be performed.
+& N/A & Using a focus class to identify global attributes limits knowledge about attributes pertaining to classes that are not the focus class.
+\\ \hline
+IF a method is a static method on Command THEN it should implement its behavior by constructing a new Command subclass instance.
+& "A method is a static method on Command" (i.e., static method ...?) & Using a focus class to identify global attributes limits knowledge about attributes pertaining to classes that are not the focus class.
+\\ \hline
+IF a class is a subclass of Command THEN it should not be public.
+& "A class is a subclass of Command" (i.e., class extends Command) & Visibility specifiers are specific to the focus class, and including attributes' negations would explode the number of attributes and potentially fog our results with uninteresting rules.
+\\ \hline
+IF a class is an Entity class or subclass THEN it must be registered in CrowdServlet by ObjectifyService. & "A class is an Entity class or subclass" & \\ \hline
+IF the save method is called THEN the now() method must be followed immediately. & "The save method is called" (i.e., call to save() function) & \\ \hline
+\end{tabular}
 
-		\subparagraph{@Entity classes must have an @id field.} IF a class has an @Entity annotation THEN it must have a field annotated with @Id.
+\caption{This table contains rules that were not found, their achievable components if they exist, and explanations of challenges to finding the complete rules.}
+\end{table}
 
-		The attributes of interest are (1) class has @Entity notation and (2) member field has annotation @id.
-With 50\% support and 80\% confidence, approximately 22\% of all FIs generated by the FP growth algorithm contained these two attributes.
+We were not able to find rules because we did not have attributes that could be used to represent those rules.
+If the rule could be represented using our attributes, then we were able to find and group those attributes.
+Attributes that we found difficult to implement were often ones that dealt with the interactions between multiple classes.
+This is because this approach generates the list of global attributes from a single input class, our focus class.
+One solution may be to use all the classes in a grouping to generate the list of global attributes to see if that can help in generating such rules.
 
-		\subparagraph{Subclasses of @Entity classes must be indexed.} IF a class is a subclass of an @Entity class THEN it needs to be indexed ('index=true').
-\tcr{[I couldn't find exact numbers on what percentages were output for these groupings.]}
+One problem that arose from the idea of using a single focus class in a grouping of classes is the idea of  ``missing" attributes; that is, attributes that we can generate if we find in the focus class but do not find or identify otherwise.
+One solution may be to include default attributes such as “is private class” and “is protected class” in the global set of attributes.
 
-		\subparagraph{@Entity classes must have a zero-argument constructor.} IF a class is an entity THEN it needs to have a zero-argument constructor.
-
-		The attributes of interest are (1) has @Entity annotation and (2) class has zero-args constructor.
-With 60\% support and 80\% confidence, approximately 20\% of the FIs generated by the FP growth algorithm contained these two attributes; as a side note, if support was lowered to 50\%, then approximately 23\% of the FIs generated contained both attributes.
-
-	\subsubsection{Artifact classes }
-		This group included all the classes that extended the Artifact class. The focus class for this group was \inlinecode{Java}{Function.java}.
-
-		\paragraph {Rules found}
-
-		\subparagraph{Artifacts should be marked as a data region with an @Entity annotation}.  IF an object is an artifact subclass THEN it needs to be an entity.
-
-		In this case, the attributes of interest are ``extends Artifact” and ``class has @Entity annotation”.
-With 60\% support and 80\% confidence, just under half of all FIs generated by the FP growth algorithm contained these two attributes.
-
-	\subsubsection{Rules not found}
-
-		\subparagraph{Creating an Artifact should be indirected through a Command.} IF a new Artifact is to be created THEN its constructor should be invoked only by its corresponding Command class.
-
-		We are not able to generate this rule because we do not create attributes that would allow us to find this rule.
-We do generate an attribute that would indicate that an Artifact object is created, and attributes indicating that there were functions in which the respective Artifact class constructor was called, but there isn’t a way to communicate the idea of invoking the Artifact constructor only with the corresponding Command class.
-
-		\subparagraph{Communication between artifacts should be indirected through a Command.} IF an Artifact needs to communicate with another artifact THEN it should create a Command describing the desired action to be performed.
-
-        We also can’t represent this rule with our current set of attributes for similar reasons as the previous rule.
-The difficult part of this rule is that we output attributes in the form “function foo() calls ECommand constructor” or “function foo() calls FCommand constructor”, which will not get associated together in a group because the names of the classes are different.
-Further, the program uses a single focus class to generate a set of global attributes that are searched for in related classes.
-Consequently, we pass the function an xml file that contains only the file for the focus class, which means we cannot find out what the parent of the current class extends since the file only contains the information for the focus class.
-
-        		\subparagraph{All Microtask commands must be handled by Command subclasses.} IF a method is a static method on Command THEN it should implement its behavior by constructing a new Command subclass instance.
-
-		Again, while we can/do output attributes for the “IF” portion of this rule, we cannot output attributes for the “THEN” portion of this rule because we only create attributes from a single input class, and therefore cannot create an attribute that represents this information.
-
-		\subparagraph{Commands should not be publicly visible.} IF a class is a subclass of Command THEN it should not be public.
-
-		While we do output visibility specifiers and inheritance information, we cannot output this rule because we only output visibility specifiers for the focus class.
-Therefore, if the focus class is public, we will output “class is public” but we will not output any attributes about private or protected classes.
-One solution is to include default attributes such as “is private class” and “is protected class” in the global set of attributes.
-Theoretically, we can find implement our attribute outputting algorithm so that this information can be output.
-However, our current method does not allow us to output attributes that could be used to represent this rule.
-
-		\subparagraph{@Entity classes must be registered in the CrowdServlet class.} IF a class is an Entity class or subclass THEN it must be registered in CrowdServlet by ObjectifyService.
-
-		Again, we cannot output this rule because of the kinds of attributes that are output by our approach.
-In order for a class to be ``registered", a function call to the register function must be made by an ObjectifyService object with the class to be registered as the argument.
-The difficulty comes in trying to track that a function call has been made by a particular class.
-Without any prior information, it is difficult to recognize which attributes should be made about which function calls in which classes.
-Since there are thousands and even hundreds of thousands of functions calls in a given code base, the scalability of trying to output information about every function call makes representing this information in attributes rather intractable.
-
-		\subparagraph{Save() calls should always be committed immediately.} IF the save method is called THEN the now() method must be followed immediately.
-
-		A similar problem to the previous rule exists to this one.
-Any number of attributes could be generated with all the possible pattern combinations of ordered function calls; however, this would cause an explosion of attributes that would likely render outputting attributes and finding associations intractable.
-One possible way of trying to find this rule might use a pattern finding technique from association rule mining.
+One final set of attributes we found difficult to encode were ones dealing with order, especially the order of function calls.
+While such rules are often important, generating the attributes for such rules often presents scalability and tractability challenges.
+One possible way of trying to find such rules might use a pattern finding technique from association rule mining.
 The database such a technique might be trained on may be in which each row represents a different function, and the attributes for each function would represent the function calls made with in that section of the code.
@@
 
+One final challenge is the challenge of determining class groupings.
+Based off of our results it is obvious that the kinds of classes that are grouped and the class chosen as the focus class can have a significant impact on the type and usefulness of the FI's (and thus the rules) that are generated.
+One option may be to group attributes based off of parent-child inheritance relationships.
+Another option may be to randomly group classes and generate FI's from those groupings until interesting and meaningful groups have been formed.
+Both of these options have yet to be explored.
+
 While prior work has been conducted with code suggestion and degree of interest models, we believe the area of mixed human-AI documentation still has much room for improvement and study in order to more accurately and more flexibly detect the design rules used in a code base.

### 2019-08-05 paper.tex
edits

@@
 
-Documentation is critical to preserving information about the choices about the design of a project and how those choices are implemented.
-However, most documentation is not updated frequently, and often only individual developers know critical pieces of information, which are integral in maintaining project coherency and forwards and backwards compatibility.
+Documentation is critical to preserving information about \textit{design rules}, which we define as the choices about the design of a project and how those choices are implemented.
+However, most documentation is not updated frequently, and often only individual developers know critical pieces of information that are integral in maintaining project coherency and forwards and backwards compatibility.
 We developed an algorithm that can represent the information contained in a code base and automatically suggest likely design rules.
-Our results demonstrate that our algorithm can successfully represent and identify significant design rules, and has the potential to be used to automatically generate documentation for a project.
+Our results demonstrate that our algorithm can successfully represent and identify significant design rules, and it furthermore has the potential to be used to automatically generate documentation for a project.
 
@@
 Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed developers.
-As code is written and a project develops, various design decisions are made, which impact both existing and future code.
-Documentation of design decisions and the rationale behind those decisions is dependent on the developer and is often recorded or dispersed between several disparate locations, including a formal document, comments in the code, and the developers themselves.
-However, documentation is often not written, read, or updated, causing developers to depend largely on the code and other sources of information rather than explicit, written documentation.
+As code is written and a project develops, various decisions about its design are made, which impact both existing and future code.
+This set of choices about the code's design and how those choices are implemented is hereon defined as  \textit{design rules}.
+Ideally, as code is authored, it should follow design rules that were previously used to author code.
+Despite their significance for present and future developers, however, design rules are rarely properly documented.
 
-Ideally, as code is authored or modified, it should follow design rules that were previously used to author code.
-The \textit{design rules} for a project are the set of choices about the code's design and how those choices are implemented.
-Several sources of information, including search history, cursor location, event logs, debugger information, and the code itself can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest.
-Some information about design rules may only be recorded in the memories of co-workers, and thus access to this kind of information is also critical for developers trying to understand and use existing code.
+Documentation of design rules is dependent on the developer and often does not exist or is rarely read or updated.
+Some information about design rules may only be recorded in the memories of co-workers.
+When documentation exists, it is often dispersed between several locations, including a formal document, comments in the code, and the developers themselves.
+In short, without proper documentation, newcomers trying to understand and use existing code are limited in access to critical information about the project's design rules.
+Rather than explicit, written documentation, they must instead depend largely on the code itself.
 
 Mixed human-AI authoring of code patterns can greatly assist developers to efficiently and accurately develop and maintain a unified set of rules.
-There are an infinite number of patterns that could be found in a given code base, and an even larger diversity of representations for those patterns; therefore, the crux of the problem lies in determining how to represent the information contained in the code base and in identifying the patterns using the chosen representation.
+Several sources of information, including search history, cursor location, event logs, debugger information, and the code itself can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest.
+There is moreover an infinite number of patterns that could be found in a given code base, and an even larger number of possible representations for those patterns; therefore, the two greatest challenges lie in determining how to represent the information contained in the code base and in identifying patterns using the chosen representation.
 Hence our focus is on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.
@@
 Section~\ref{results} contains a description of the results for our algorithm, followed by a description of the tool interface in Section~\ref{toolInterface}.
-Finally, we discuss the short comings of our algorithm and related in works in Sections~\ref{relatedWorks} and Sections~\ref{disc}, respectively.
+Finally, we discuss the shortcomings of our algorithm and related works in Sections~\ref{relatedWorks} and Sections~\ref{disc}, respectively.
 
@@
 Consequently, we assume the developers for which we are designing our algorithm have some general familiarity with the code and can identify proper design rules if supplied with a set of rules to consider.
-Thus, feedback form the developer about hypothesized rules is dependable, enabling mixed human-AI rule authoring.
+Thus, feedback from the developer about hypothesized rules is dependable, enabling mixed human-AI rule authoring.
 
@@
 
-	Part of knowing which sources are most useful for deriving information about design rules is understanding where developers themselves look for information about a project and what kinds of information are useful to programmers.
+	Part of knowing which sources are most useful for deriving information about design rules is understanding where developers themselves look for information about a project and what kinds of information are actually useful to programmers.
 
@@
 Researchers who investigated how programmers read and explore code have found that programmers' activities include checking implementation details, checking common style, and browsing.
-Programmers also performed code search to understand various dependencies within and between projects, why something is failing, and the side effects of a proposed changed \cite{SadowskiEtAl2015}.
+Programmers also performed code search to understand various dependencies within and between projects, why something is failing, and the side effects of a proposed change \cite{SadowskiEtAl2015}.
 
-Ko et al investigate what sources of information developers use to accomplish a task and how that information affects developers' workflow throughout the day.
-They report that developers look at a variety of sources to accomplish a task, including check-in logs, bug reports, content management systems, version control systems, and other coworkers.
-Additionally, they identify knowledge about design and program behavior as the type of information that is most often deferred since unavailable coworkers are often the only source of knowledge.
+Ko et al in particular investigate what sources of information developers use to accomplish a task and how that information affects developers' workflow throughout the day.
+They report that developers consult with a variety of sources to accomplish a task, including check-in logs, bug reports, content management systems, version control systems, and other coworkers.
+Additionally, they identify knowledge about design and program behavior as the type of information that is most often deferred since coworkers who are unavailable are also often the only source of knowledge.
 Developers sought out coworkers most often when there were information needs with regards to code design.
@@
 Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree of interest model to reflect developers' knowledge of code \cite{FritzEtAl2007}.
-The researchers' model was based on the total number of interactions the programmer has with an element and the recency of that interaction.
+The researchers' model was based on the total number of interactions the programmer had with an element and the recency of that interaction.
 Other factors they identified that could be used to improve their model included authorship of program elements, the role of elements, and the task being performed \cite{FritzEtAl2007}.
@@
 However, we focus on trying to find rules using only the code base and direct feedback from the developer.
-The reason for this decision is that the code base and direct feedback are the only two sources of information that we are guaranteed.
+The reason for this decision is that the code base and direct feedback are the only two sources of information that are guaranteed to exist.
 Future iterations of this algorithm may also use these other sources of information to generate design rules.
@@
 Ideally, we would output information only about the most critical features of the code base that can lead us to the most likely design rules.
-However, the code base contains a lot of information and there are many ways of representing that information.
+However, the code base contains a lot of potentially critical information and there are many ways of representing that information.
 Additionally, there are scalability concerns since code bases can easily have over a quarter million lines of code.
@@
 
-The challenge then is what kinds of attributes to generate (that is, what kinds of representations for the code to use), since there are many different ways to represent the features of a code base (see Figure~\ref{fig:attrEx}).
+The challenge then is what kinds of attributes to generate (that is, what kinds of representations for the code to use), since there are many different ways to represent the features of a code base (Figure~\ref{fig:attrEx}).
 Consequently, there are many ways to represent a design rule (Figure~\ref{fig:drEx}).
@@
   \includegraphics[width=\linewidth]{attributeEx.png}
-  \caption{There are many different attributes that can be created that represent different features of the code in different ways.}
+  \caption{There are many different attributes that can be created to represent different features of the code in different ways.}
   \label{fig:attrEx}
@@
 
-	The basic idea in this approach is that we would have a set of reserved item IDs corresponding to “default” attributes that we know we always have a chance of finding.
-For example, there is always the chance that there is a public class; thus, there is a reserved item ID corresponding to an attribute titled “is a public class”.
-We also output attributes that are specialized to the code base from which they are derived, such as annotations that are on classes and what classes are involved in an inheritance structure.
-Each line output to the database represented the set of attributes belonging to a different class in the code base.
+	The basic idea in this approach is that we reserve a set of item IDs corresponding to “default” attributes that we know we always have a chance of finding.
+For example, there is always the chance that there is a public class; thus, there is a reserved item ID corresponding to an attribute titled “is a public class.” We also output attributes that are specialized to the code base from which they are derived, such as annotations that are on classes and names of classes that are involved in an inheritance structure.
+Each line output to the database represents the set of attributes belonging to a different class in the code base.
 
@@
 
-	The second approach entailed generating several databases that could be further mined for more detailed information.
+	The second approach entails generating several databases that could be further mined for more detailed information.
 The logic behind this approach is that it might be easier to output more specific attributes for different subsets of the data that are related, and thus find more specific and interesting rules.
-Each starting database would have rows composed of different subsets of the data that are related.
+Each starting database has rows composed of different subsets of the data that are related.
 For example, one database might contain more specific attributes related to subclasses, with each row in the database representing a different subclass.
-Other output databases may have rows composed of the different functions in a class, and another would have rows representing different subclasses.
-Once these databases are generated, association rules would be derived from them.
+Other output databases may have rows composed of the different functions in a class, and another might have rows representing different subclasses.
+Once these databases are generated, association rules are derived from them.
 Based off the association rules that are created, a second more detailed database might be created in order to mine more specific information about the rule.
-For example, the database with rows made from distinct functions might generate a rule that says “IF there is a function that returns the call from a constructor
-THEN it needs to return a specific type $<$type name$>$.” The second database created would be composed of rows all of which are functions that return the call from a constructor and return the specific type.
+For example, the database with rows made from distinct functions might generate a rule that says “IF there is a function that returns the call from a constructor THEN it needs to return a specific type $<$type name$>$.” The second database created would be composed of rows, all of which are functions that return the call from a constructor and return the specific type.
 Attributes for the derived database could include more specific characteristics about the constructor, such as the parameters required by the constructor and the type of object created by the constructor.
@@
 The main advantage to outputting the attributes in classes this way is that it is more scalable.
-Since the set of global attributes is compiled only of the attributes of a single class, a greater number of attributes can be output without significantly decreasing efficiency or scalability.
+Since the set of global attributes is composed only of the attributes of a single class, a greater number of attributes can be output without significantly decreasing efficiency or scalability.
 
@@
 However, in this approach we also output more specific attributes that contain information about multiple features.
-Attributes specifically include annotations on classes, functions, and fields complete with the annotation name and arguments, constructors storing all of the values passed as arguments in member variables, constructors having empty bodies or non-empty bodies, the return types of functions.
+Attributes specifically include annotations on classes, functions, and fields complete with the annotation name and arguments; constructors storing all of the values passed as arguments in member variables; constructors having empty bodies or non-empty bodies, and; the return types of functions.
 
@@
 
+% what is this??
 \makebox[\textwidth]{attributeFunctions.png}
@@
 \includegraphics[width=\linewidth]{attributeFields.png}
-\caption{A comparison of the attributes regarding functions produced by Approach 1, 2, and 3.}
+\caption{A comparison of the attributes regarding member fields produced by Approach 1, 2, and 3.}
 \label{fig:attrField}}
@@
 \subsubsection{Associating attributes}
-	We chose the Frequent-Pattern (FP) Growth Algorithm, which is an algorithm frequently used in association rule mining (ARM).
+	We choose the Frequent-Pattern (FP) Growth Algorithm, which is an algorithm frequently used in association rule mining (ARM).
 ARM seeks to mine databases for patterns of items that frequently occur together.
-It is often used in market basket analysis to see what products are often purchased simultaneously.
-FP Growth is a type of association rule mining algorithm that efficiently finds frequent itemsets (FIs) by storing their patterns in a tree data structure.
-Advantages of the FP Growth algorithm include:
+It is often used in market basket analysis to see what products are often purchased together, for example.
+FP Growth is a type of association rule mining algorithm that can efficiently find rules or simply frequent itemsets (FIs) by storing their patterns in a tree data structure.
+Advantages of the FP Growth algorithm include its:
 	\begin{itemize}
-		\item It’s designed to find hidden patterns among items.
-		\item Its scalability and relative efficiency.
-		\item Various implementations that deal with sparse data already exist.
+		\item ability to find hidden patterns among items.
+		\item scalability and relative efficiency.
+		\item various existing implementations that deal with high dimensionality and sparse data.
 	\end{itemize}
-In our case, the items in the FIs output by the algorithm are groups of attributes that frequently appear together in the code base.
 
@@
 	\begin{enumerate}
-		\item Support - the joint probability of two or more items.
-		\item Confidence - the conditional probability of two or more items.
+		\item \textit{Support} - the joint probability of two or more items.
+		\item \textit{Confidence} - the conditional probability of two or more items.
 	\end{enumerate} 
 Both are typically expressed as percentages ranging from 0-100\%, and are used to produce FIs that occur with a particular frequency.
-The support and frequency are used to fine tune the algorithm and varying them can result in finding different FIs.
+The support and confidence are used to fine tune the algorithm, and varying them can result in finding different FIs and rules.
+
+We use an algorithm called Node-FPGrowth which only finds FIs, and in our case, the items in the FIs output are groups of attributes that frequently appear together in the code base.
+
+% citation needed
 
@@
 
-Once the FIs have been produced an extension of the algorithm produces association rules.
+Once the FIs have been produced, an extension of the algorithm produces association rules.
 Items in an association rule are either in the antecedent (``IF") portion of the rule or the consequent (``THEN") portion of the rule.
@@
 We use the association rules produced from the algorithm as our candidate design rules to present to the developer.
+
+% remove this section altogether?
 
@@
 	\subsection{Approach 1}
-	This approach was not successful even when used with lower support (20-40\%).
-The general problem was that associations produced from this database were uninteresting and obvious.
-For example, many of the rules produced were rules such as, “IF it is a public class THEN it has a public function” or “IF it is a class with annotation @$<$class name$>$ THEN it is a class that has an annotation”.
+	This approach was unsuccessful, even when used with lower support (20-40\%).
+Associations produced from this database were generally uninteresting and obvious.
+For example, many of the rules produced were rules such as, “IF it is a public class THEN it has a public function,” or “IF it is a class with annotation @$<$class name$>$ THEN it is a class that has an annotation.”
 
@@
 	\subsection{Approach 2}
-	The main prohibiting factor in this approach, is the total number of tables created and the total number of times the code would need to be traversed to create all of the tables.
-Consequently, we found this approach to be impractical, and did not seek to pursue this approach further.
+	The main prohibiting factor in this approach is the total number of tables created and the total number of times the code would need to be traversed to create all of the tables.
+Consequently, we found this approach to be impractical and did not pursue this approach further.
 
@@
 We present the groups of classes that were successfully used to identify one of our target design rules.
-Under each group of classes, we list the rules that we found along with an explanation.
+Under each group of classes, we list the rules that we found along with their decompositions as target attributes and the percentages of FIs containing all target attributes.
 A discussion of what rules could not be discovered and why follows this portion.
@@
 
-	We used support 60\% for all our tests, except for the test used to generate the rule ``IF a class has an @Entity annotation THEN it must have a field annotated with @Id"; a support of 50\% was used.
-Lowered support was used to restrict the number of FI's produced by the algorithm.
-Although confidence is used in many ARM techniques, it is not used in generating FI's; thus, we did not have to specify a confidence level for the algorithm.
+	We used 60\% support for all tests, except for the test used to generate the rule ``IF a class has an @Entity annotation THEN it must have a field annotated with @Id"; a support of 50\% was used instead.
+Lowered support was necessary because otherwise, the attributes did not occur frequently enough to appear as FIs.
+Although confidence is used in many ARM techniques, it is not used in generating FIs; thus, we did not have to specify a confidence level for the algorithm.
+
+	Also note that the rule "IF an object is an artifact subclass THEN it needs to be an entity" reports a more approximate result than other rule because the algorithm timed out before finishing generating the entire set of frequent itemsets.
 
@@
 \multicolumn{3}{|l|}{Peripheral classes: Command class and classes that extend Command} \\\hline
-Rule & Attributes & \% FI that contain \\\hline
+Rule & Attributes & \% FIs \\\hline
 \end{tabular}
@@
 \begin{tabular}{| >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
-\multicolumn{3}{|l|}{\textcoloryellow{\textbf{DTO classes and subclasses}}} \\\hline
+\multicolumn{3}{|l|}{\textcoloryellow{\textbf{DTO classes*, subclasses**}}} \\\hline
 \multicolumn{3}{|l|}{Focus class: FunctionInFirebase.java} \\\hline
-\multicolumn{3}{|l|}{Peripheral classes: classes that extend DTO and subclasses of classes that extend DTO} \\\hline
-Rule & Attributes & \% FI that contain \\\hline
+\multicolumn{3}{|l|}{*Peripheral classes: classes that extend DTO} \\\hline
+Rule & Attributes & \% FIs \\\hline
 \end{tabular}
@@
 & (1) class extends DTO \newline (2) class has zero-args constructor \newline (3) class has empty body & 6.5\%\\\hline
+\multicolumn{3}{|l|}{**Peripheral classes: classes that extend DTO and subclasses of classes that extend DTO} \\\hline
 IF a class is a DTO object THEN it needs to have a zero-argument constructor with an empty body.
@@
 \multicolumn{3}{|l|}{Peripheral classes: classes that have the @Entity annotation placed directly above them} \\\hline
-Rule & Attributes & \% FI that contain \\\hline
+Rule & Attributes & \% FIs \\\hline
 \end{tabular}
@@
 \multicolumn{3}{|l|}{Peripheral classes: classes that extend Artifact class} \\\hline
-Rule & Attributes & \% FI that contain \\\hline
+Rule & Attributes & \% FIs \\\hline
 \end{tabular}
@@
 \begin{tabular}{| >{\arraybackslash}m{6.5cm} | >{\arraybackslash}m{6.5cm} | >{\centering\arraybackslash}m{2.5cm} |}
-IF an object is an artifact subclass THEN it needs to be an entity. & (1) extends Artifact \newline (2) class has @Entity annotation & 49.8\% \\\hline
+IF an object is an artifact subclass THEN it needs to be an entity. & (1) extends Artifact \newline (2) class has @Entity annotation & \~{}49.8\% \\\hline
 \end{tabular}
@@
 \end{table}
+Each of these rules could be represented using the attributes that we encoded from the CrowdCode database, and we were able to find these attributes in the FIs generated using the FP Growth algorithm.
+Rules that are found most often (had the largest percentage found in the FIs that are generated) tend to be rules in which the total number of classes in the group was moderately large, and the attributes shared between different classes overlaps but still vary moderately.
+
+Furthermore, we found that while a great number of attributes was often generated by the algorithm, the number of those attributes found in the peripheral classes and output to the database was significantly less.
+Usually, over a hundred attributes would be included in the global list but about 20 different attributes would be found in the peripheral classes.
+In one case, over eight hundred total attributes were found in the focus class, but it shared only about 30 attributes with its peripheral classes.
+Thus, many FI's produced were fairly similar, differing in only a few attributes.
 
@@
 \hline
-Rule & Achievable & Challenge \\ \hline
+Rule & Achievable & Challenge(s) \\ \hline
 \end{tabular}
-
-Each of these rules could be represented using the attributes that we encoded from the CrowdCode database, and we were able to find these attributes in the FI's generated using the FP Growth algorithm.
-Rules that are found most often (had the largest percentage found in the FI's that are generated) tend to be rules in which the total number of classes in the group was moderately large, and the attributes shared between different classes overlaps but still vary moderately.
-
-Furthermore, we found that while a great number of attributes was often generated by the algorithm, the number of those attributes found in the peripheral classes and output to the database was significantly less.
-Usually, over a hundred attributes would be included in the global list but about 20 different attributes would be found in the peripheral classes.
-In one case, over eight hundred total attributes were found in the focus class, but it shared only about 30 attributes with its peripheral classes.
-Thus, many FI's produced were fairly similar, differing in only a few attributes.
 
@@
 \\ \hline
-IF a class is an Entity class or subclass THEN it must be registered in CrowdServlet by ObjectifyService. & "A class is an Entity class or subclass" & \\ \hline
-IF the save method is called THEN the now() method must be followed immediately. & "The save method is called" (i.e., call to save() function) & \\ \hline
+IF a class is an Entity class or subclass THEN it must be registered in CrowdServlet by ObjectifyService.
+& "A class is an Entity class or subclass" & Registering a class must be done by a certain object with a specific argument, so the scalability of outputting information about every function call made by different classes makes representing this information intractable.
+\\ \hline
+IF the save method is called THEN the now() method must be followed immediately.
+& "The save method is called" (i.e., call to save() function) & There may be hundreds of thousands of function calls in a given code base, so the scalability of outputting information about their sequential orders makes representing this information intractable.
+\\ \hline
 \end{tabular}
@@
 They developed a statistical language model to aid in providing suggestions for different code snippets \cite{RaychevEtAl2014}.
-We could think of our challenge as analogous to an NLP problem that aims to outline to a corpus of text or maybe, even more abstractly, find rhetorical devices in a text.
+We could think of our challenge as analogous to an NLP problem that aims to outline a corpus of text or maybe, even more abstractly, find rhetorical devices in a text.
 Alternatively, we could simply rely more on traditional papers and research that have been conducted in this area that do not rely on NLP techniques to provide solutions.
-Both perspective may prove useful in the initial stages of research that entail exploring different ways that information is stored and what information about developer activity has seemed most helpful in designing related tools.
+Both perspectives may prove useful in the initial stages of research that entail exploring different ways that information is stored and what information about developer activity has seemed most helpful in designing related tools.
 
@@
 
-Many tools and methods have been devised to augment programmers' ability to accomplish a task including code recommender systems for novices \cite{HartmannEtAl2010}, search tools for identifying bugs \cite{HovemeyerPugh2004}, search tools for identifying relevant API functions and the sections of code that need to be altered \cite{RongEtAl2016}, and code suggestion \cite{RaychevEtAl2014}.
-However, one area that seems largely unexplored is tools that facilitate the documentation of code.
+Many tools and methods have been devised to augment programmers' abilities to accomplish a task including code recommender systems for novices \cite{HartmannEtAl2010}, search tools for identifying bugs \cite{HovemeyerPugh2004}, search tools for identifying relevant API functions and the sections of code that need to be altered \cite{RongEtAl2016}, and code suggestion \cite{RaychevEtAl2014}.
+However, one area that seems largely unexplored is tools that facilitate the automated documentation of code.
 
@@
 In this paper, we present three different approaches for outputting attributes about a project code base.
-The results show that using the third approach we can have a flexible representation of  many design rules that we might wish to find in a code base.
+The results show that, using the third approach, we can have a flexible representation of many design rules that we might wish to find in a code base.
 They also show that there seems to be a tractable and fast way of analyzing code to detect design rules.
 
-There are several rules kinds of attributes that we cannot represent, and, thus, we cannot find design rules that include those attributes.
-Attributes we still cannot represent are ones that include tracking sequential function calls and constructor calls across and within broad categories classes.
+There are several kinds of attributes that we cannot represent, and, thus, we cannot find design rules that include those attributes.
+Attributes we still cannot represent are ones that include tracking sequential function calls and constructor calls across and within broad categories of classes.
 Outputting these attributes usually present tractability problems and may require a different representation and algorithm in order to be detected.
@@
 One final challenge is the challenge of determining class groupings.
-Based off of our results it is obvious that the kinds of classes that are grouped and the class chosen as the focus class can have a significant impact on the type and usefulness of the FI's (and thus the rules) that are generated.
+Based off of our results, it is obvious that the kinds of classes that are grouped and the class chosen as the focus class can have a significant impact on the type and usefulness of the FIs (and thus the rules) that are generated.
 One option may be to group attributes based off of parent-child inheritance relationships.
